title: "GTCI Figures"
author: "Emerson Johnston"
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = FALSE,
  warning   = FALSE,
  message   = FALSE,
  fig.width  = 8.0,
  fig.height = 5.5,
  dpi       = 300,
  fig.align = "center",
  dev       = "ragg_png"
)

library(tidyverse)
library(scales)
library(showtext)
library(ggtext)
library(ggrepel)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(gt)
library(gtExtras)
library(webshot2)
library(magick)
library(pdftools)

source("R/theme.R")
source("R/helpers.R")
source("R/tables.R")
source("R/chart_layers.R")
source("R/maps.R")
```

# Figure 01 - Total STEM Degree Completition in the United States, by Level (1995 - 2024)
```{r figure 0001}
meta <- get_meta("fig_001")

df_001 <- read_levels("fig_001", value_col = "Count",
                      levels_order = c("Doctorate", "Masters", "Bachelors"))

fig_001 <- ggplot(df_001, aes(Year, Count, fill = Level)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_001$Year) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_y_continuous(breaks = c(250000, 500000, 750000),
                   labels = label_comma(),
                   expand = EXPAND_BAR) +
  scale_fill_levels(reverse_legend = FALSE) +
  labs_meta(meta, y = "Degrees awarded") +
  theme_tpa()

save_chart(fig_001, "fig_001")
```

# Figure 02 - STEM Degrees Awarded as a Share of Total Degrees Awarded - All levels
```{r figure 002}
meta <- get_meta("fig_002")
pct  <- label_percent(accuracy = 1)
df_002 <- read_levels(
  "fig_002",
  value_col    = "Share",
  levels_order = c("Bachelors", "Masters",
                   "All Doctorates (IPEDS)")
) %>%
  filter(!is.na(Share))

last_002  <- last_by_group(df_002, Year, Level)
first_002 <- df_002 %>% group_by(Level) %>% slice_min(Year, n = 1) %>% ungroup()

fig_002 <- ggplot(df_002, aes(Year, Share, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = last_002,
    mapping      = aes(label = paste0(pct(Share), " - ", Level)),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  geom_label_repel_tpa(
    data         = first_002,
    mapping      = aes(label = pct(Share)),
    nudge_x      = -0.5,
    hjust        = 1,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_continuous(
    breaks = seq(min(df_002$Year), max(df_002$Year), 2),
    expand = expansion(mult = c(0.05, .5))
  ) +
  scale_y_continuous(labels = pct, expand = EXPAND_LINE_WIDE) +
  scale_color_levels() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of completions") +
  theme_tpa()
save_chart(fig_002, "fig_002")
```

# Figure 03 - Trends in Research Doctorate Recipients from U.S. Colleges and Universities, All Fields, by Year (1958-2023)
```{r figure 003}
meta <- get_meta("fig_003")

df_003 <- read_fig("fig_003") %>%
  select(Year, value = 2) %>%
  mutate(across(everything(), as.numeric))

labels_003 <- first_last_peak(df_003, Year, value)

fig_003 <- ggplot(df_003, aes(Year, value)) +
  geom_line(linewidth = LINE_WIDTH, color = tpa_colors[1]) +
  geom_label_repel_tpa(
    data         = labels_003,
    mapping      = aes(label = fmt_num_k(value)),
    color        = tpa_colors[1],
    nudge_y      = 3000,
    with_segment = TRUE
  ) +
  scale_x_years(df_003$Year) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_LINE_TALL) +
  labs_meta(meta, y = "Doctorate recipients") +
  theme_tpa()

save_chart(fig_003, "fig_003")
```

# Figure 04 - Trends in All Research Doctorate Recipients from U.S. Colleges and Universities, by Year and by Broad Science and Engineering Field (2014-2024)
```{r figure 004}
meta <- get_meta("fig_004")

df_004 <- read_fig("fig_004") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Field", values_to = "Count") %>%
  group_by(Field) %>%
  mutate(baseline = Count[Year == min(Year)],
         pct_change = (Count / baseline - 1) * 100) %>%
  ungroup()

fig_004 <- ggplot(df_004, aes(Year, Field, fill = pct_change)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = sprintf("%+.0f%%", pct_change),
                color = abs(pct_change) > 10),
            size = DATA_LABEL_SIZE * 0.8 / .pt,
            family = FONT_FAMILY) +
  scale_x_continuous(breaks = seq(min(df_004$Year), max(df_004$Year), 1),
                   expand = EXPAND_NONE) +
  scale_y_discrete(expand = EXPAND_NONE) +
  scale_fill_gradientn(
    colors = c(tpa_colors[2], HEATMAP_MID, tpa_colors[1]),
    values = scales::rescale(c(min(df_004$pct_change),
                               0,
                               max(df_004$pct_change))),
    labels = function(x) sprintf("%+.0f%%", x)) +
  scale_color_manual(values = c("TRUE" = "white", "FALSE" = "grey25"),
                     guide = "none") +
  labs_meta(meta, x = NULL, y = NULL) +
  labs(fill = "% change\nfrom 2014") +
  theme_heatmap()

save_chart(fig_004, "fig_004")
```

# Figure 05 - International Student Share of STEM Degree Completions
```{r figure 005}
meta <- get_meta("fig_005")
pct  <- label_percent(accuracy = 1)
df_005 <- read_levels(
  "fig_005",
  value_col    = "Share",
  levels_order = c("Bachelors", "Masters",
                   "All Doctorates (IPEDS)", "Research Doctorates (SED)")
) %>%
  filter(!is.na(Share))

last_005  <- last_by_group(df_005, Year, Level)
first_005 <- df_005 %>% group_by(Level) %>% slice_min(Year, n = 1) %>% ungroup()

fig_005 <- ggplot(df_005, aes(Year, Share, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = last_005,
    mapping      = aes(label = paste0(pct(Share), ": ", Level)),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  geom_label_repel_tpa(
    data         = first_005,
    mapping      = aes(label = pct(Share)),
    nudge_x      = -0.5,
    hjust        = 1,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_continuous(
    breaks = seq(min(df_005$Year), max(df_005$Year), 2),
    expand = expansion(mult = c(0.05, .5))
  ) +
  scale_y_continuous(labels = pct, expand = EXPAND_LINE_WIDE) +
  scale_color_levels() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of completions") +
  theme_tpa()
save_chart(fig_005, "fig_005")
```

# Figure 06 - Share of Degree Completions by U.S. Nonresidents, by Award Level and Field (2003-2023)
```{r figure 006, fig.height=10, fig.width=10}
meta <- get_meta("fig_006")

df_006 <- read_fig("fig_006") %>%
  mutate(
    Year   = as.numeric(Year),
    Share  = as.numeric(NonresidentShare),
    Degree = factor(Degree, levels = c("Bachelors", "Masters", "Doctorate"))
  )


fields_drop <- c(
  "Agricultural/Animal/Plant/Veterinary Science and Related Fields"
)

eng_fields <- c(
  "Engineering",
  "Engineering/Engineering-Related Technologies/Technicians"
)

df_006d <- df_006 %>%
  filter(!Field %in% fields_drop) %>%
  mutate(Field = if_else(Field %in% eng_fields, "Engineering", Field)) %>%
  group_by(Field, Degree, Year) %>%
  summarise(Share = mean(Share, na.rm = TRUE), .groups = "drop")

# first/last year change, by degree, wide across degrees
first_yr <- min(df_006d$Year)
last_yr  <- max(df_006d$Year)

tab006d_all <- df_006d %>%
  filter(Year %in% c(first_yr, last_yr)) %>%
  pivot_wider(names_from = Year, values_from = Share) %>%
  rename(FirstYear = !!as.character(first_yr),
         LastYear  = !!as.character(last_yr)) %>%
  mutate(PctChangeInShare = (LastYear - FirstYear) / FirstYear * 100)

tab006_wide <- tab006d_all %>%
  pivot_wider(
    id_cols     = Field,
    names_from  = Degree,
    values_from = c(FirstYear, LastYear, PctChangeInShare),
    names_glue  = "{Degree}_{.value}"
  ) %>%
  select(Field,
         starts_with("Bachelors_"),
         starts_with("Masters_"),
         starts_with("Doctorate_"))

write.csv(tab006_wide, "data/tab_006d.csv", row.names = FALSE)

fig_006 <- ggplot(df_006, aes(Year, Share, color = Degree)) +
  geom_hline(yintercept = 50, color = tpa_colors[1],
             linetype = "dashed", linewidth = LINE_WIDTH_REF, alpha = 0.6) +
  geom_line(linewidth = LINE_WIDTH_DENSE) +
  geom_point(size = 1) +
  facet_wrap(~ Field, ncol = 2, scales = "fixed") +
  scale_x_years(df_006$Year) +
  scale_y_continuous(limits = c(0, 100),
                   breaks = c(0, 25, 50, 75, 100),
                   labels = label_number(suffix = "%"),
                   expand = EXPAND_NONE) +
  scale_color_levels() +
  labs_meta(meta, y = "Nonresident share of completions") +
  theme_facet()

save_chart(fig_006, "fig_006", size = "long")
```

# Figure 07 - Projected Annual STEM PhD Production Per 100,000 of the 20- to 34-year-old population, by Country, 2011–2050
```{r figure 007}
meta <- get_meta("fig_007")

df_007 <- read_fig("fig_007") %>%
  pivot_observed_projected() %>%
  order_by_latest(Country, value)

labels_007 <- last_by_group(df_007, Year, Country)
proj_start <- proj_start_year(df_007)
y_max      <- max(df_007$value)

fig_007 <- ggplot(df_007, aes(Year, value, color = Country, group = Country)) +
  annotate_projected(proj_start, max(df_007$Year),
                     label_y = y_max * 0.98) +
  geom_op_lines(df_007) +
  geom_label_repel_tpa(
    data    = labels_007,
    mapping = aes(label = paste0(
      if_else(Country == "United Kingdom", "United\nKingdom", as.character(Country)),
      ": ", round(value)
    )),
    nudge_x    = 2,
    hjust      = 0,
    lineheight = 0.85,
    with_segment = TRUE
  ) +
  scale_x_years(df_007$Year, pad_right = PAD_RIGHT_NARROW) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "STEM PhDs per year") +
  theme_op()

save_chart(fig_007, "fig_007")
```

# Figure 08 - Projected Absolute Annual STEM PhD Production by Country, 2011–2050
```{r figure 008}
meta <- get_meta("fig_008")

df_008 <- read_fig("fig_008") %>%
  pivot_observed_projected() %>%
  order_by_latest(Country, value)

labels_008 <- last_by_group(df_008, Year, Country)
proj_start <- proj_start_year(df_008)
y_top      <- y_top_round(df_008$value, 50000)

milestones <- tribble(
  ~year, ~label,
  2019, "China Tops US in STEM PhDs",
  2033, "India Tops US in STEM PhDs",
  2042, "India Tops China in STEM PhDs, Both now produce 1.5x US",
  2050, "India Doubles US STEM Production"
)

fig_008 <- ggplot(df_008, aes(Year, value, color = Country, group = Country)) +
  annotate_projected(proj_start, max(df_008$Year) + 0.5,
                     ymax = y_top, label_y = y_top * 0.92) +
  geom_op_lines(df_008) +
  annotate_milestones(
    milestones, y_top,
    bg_for = \(year) if_else(year >= proj_start, "grey94", "white")
  ) +
  geom_label_repel_tpa(
    data         = labels_008,
    mapping      = aes(label = Country),
    nudge_x      = 2,
    hjust        = 0,
    with_segment = TRUE
  ) +
  scale_x_years(df_008$Year, pad_right = PAD_RIGHT_NARROW) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "STEM PhDs per year") +
  theme_op()

save_chart(fig_008, "fig_008")
```

# Figure 09 - International Students in US Higher Education - Total Enrollment and Share, 1949-2025
```{r figure 009}
meta <- get_meta("fig_009")

df_009 <- read_fig("fig_009") %>%
  rename(Year = 1, Total = 2, Share = 3) %>%
  mutate(across(everything(), as.numeric),
         Share = fill_gaps(Year, Share))

scale_factor <- dual_axis_scale(
  primary_max   = max(df_009$Total, na.rm = TRUE),
  secondary_max = 0.07
)

fig_009 <- ggplot(df_009, aes(Year)) +
  geom_col(aes(y = Total, fill = "Total"),
           width = 0.7, alpha = ALPHA_COL_LIGHT) +
  geom_line(aes(y = Share * scale_factor, color = "Share"),
            linewidth = LINE_WIDTH, na.rm = TRUE) +
  scale_x_years(df_009$Year) +
  scale_y_continuous(
    name   = "Count of international students",
    labels = label_comma(),
    expand = EXPAND_BAR,
    sec.axis = sec_axis_scaled(scale_factor,
                               name   = "Share of total US enrollment",
                               labels = label_percent(accuracy = 1))
  ) +
  scale_fill_manual(name = NULL, values = c("Total" = tpa_colors[2])) +
  scale_color_manual(name = NULL, values = c("Share" = tpa_colors[1])) +
  labs_meta(meta) +
  theme_dual_axis()

save_chart(fig_009, "fig_009")
```

# Figure 10 - Economic Contributions of International Students to the U.S. Economy, 1999-2024
```{r figure 010}
meta <- get_meta("fig_010")

df_010 <- read_fig("fig_010") %>%
  rename(value = 2) %>%
  mutate(Year  = as.numeric(Year),
         value = as.numeric(value) / 1e9)

labels <- first_last_peak(df_010, Year, value)

fig_010 <- ggplot(df_010, aes(Year, value)) +
  geom_col(fill = tpa_colors[1], width = 0.7, alpha = ALPHA_COL) +
  geom_text_tpa(data    = labels,
                mapping = aes(label = sprintf("%.2f", value)),
                color   = tpa_colors[1]) +
  scale_x_years(df_010$Year, by = 1) +
  scale_y_continuous(labels = label_dollar(suffix = "B"),
                     expand = EXPAND_BAR_TALL) +
  labs_meta(meta, y = "USD (billions)") +
  theme_tpa()

save_chart(fig_010, "fig_010")
```

# Figure 11 - International Students in STEM in US Higher Education - Total Enrollment and Share, 1998-2024
```{r figure 011}
meta <- get_meta("fig_011")

df_011 <- read_fig("fig_011") %>%
  rename(
    Year           = 1,
    Total          = 2,
    STEM           = 3,
    SocialSci      = 4,
    STEM_Share     = 5,
    Combined_Share = 6
  ) %>%
  mutate(across(everything(), as.numeric))

df_bars <- df_011 %>%
  select(Year, STEM, SocialSci) %>%
  pivot_longer(-Year, names_to = "Category", values_to = "Count") %>%
  order_by_total(Category, Count) %>%
  mutate(Category = fct_recode(Category, "Social Science" = "SocialSci"))

df_lines <- df_011 %>%
  select(Year, STEM_Share, Combined_Share) %>%
  pivot_longer(-Year, names_to = "ShareType", values_to = "Share") %>%
  order_by_total(ShareType, Share) %>%
  mutate(ShareType = fct_recode(ShareType,
                                "STEM share"                 = "STEM_Share",
                                "STEM + Social Science share" = "Combined_Share"))

labels_lines <- fl_by_group(df_lines, Year, Share, ShareType)

scale_factor <- dual_axis_scale(primary_max = 800000, secondary_max = 0.60)

fig_011 <- ggplot() +
  geom_col(data = df_bars,
           aes(Year, Count, fill = Category),
           width = 0.7, alpha = ALPHA_COL) +
  geom_line(data    = df_lines,
            aes(Year, Share * scale_factor, color = ShareType),
            linewidth = LINE_WIDTH) +
  geom_text(data = labels_lines,
            aes(Year, Share * scale_factor,
                label = label_percent(accuracy = 1)(Share),
                color = ShareType),
            vjust       = -0.9,
            size        = DATA_LABEL_SIZE / .pt,
            fontface    = "bold",
            family      = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_years(df_011$Year, by = 1, pad_right = PAD_RIGHT_TIGHT) +
  scale_y_continuous(
    name   = "International student enrollments",
    labels = label_comma(),
    expand = EXPAND_BAR_TALL,
    sec.axis = sec_axis_scaled(scale_factor,
                               name   = "Share of total international enrollment",
                               labels = label_percent(accuracy = 1))
  ) +
  scale_fill_stacked(n = 2, ordinal = TRUE) +
  scale_color_stacked(n = 2, ordinal = TRUE) +
  labs_meta(meta) +
  theme_dual_axis()

save_chart(fig_011, "fig_011")
```

# Figure 12 - Trends in Regional Distribution of International Students in the United States, 1999/2000 – 2024/25
```{r figure 012}
meta <- get_meta("fig_012")

df_012 <- read_fig("fig_012") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Region", values_to = "Count") %>%
  filter(!is.na(Count),
         !Region %in% c("Stateless", "Percent Asia")) %>%
  order_by_total(Region, Count)

asia_labels <- df_012 %>%
  group_by(Year) %>%
  mutate(share = Count / sum(Count)) %>%
  ungroup() %>%
  filter(Region == "Asia") %>%
  filter(Year %in% range(Year))

fig_012 <- ggplot(df_012, aes(Year, Count, fill = Region)) +
  geom_area(alpha = ALPHA_AREA) +
  geom_text(
    data = asia_labels,
    aes(Year, Count * .87,
        label = label_percent(accuracy = 1)(share),
        hjust = if_else(Year == min(Year), 0, 1)),
    nudge_x     = c(0.3, -0.3),
    color       = "white",
    fontface    = "bold",
    family      = FONT_FAMILY,
    size        = DATA_LABEL_SIZE / .pt,
    inherit.aes = FALSE
  ) +
  scale_x_years(df_012$Year, by = 1) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_stacked(n = 7) +
  labs_meta(meta, y = "International students enrolled") +
  theme_tpa()

save_chart(fig_012, "fig_012")
```

# Figure 13 - Trends in International Student Enrollment in STEM Fields in U.S. Higher Education, by Country (2009–2024)
```{r figure 013}
meta <- get_meta("fig_013")

df_013 <- read_fig("fig_013") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_013 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 6) %>%
  pull(Country)

df_013 <- df_013 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_013 <- last_by_group(df_013, Year, Country)

fig_013 <- ggplot(df_013, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_013,
    mapping      = aes(label = paste0(Country, ": ", label_comma()(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_013$Year, pad_right = .3) +
  scale_y_log10(labels = label_comma(),
                breaks = c(1000, 5000, 10000, 50000, 100000, 250000),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Enrolled students (log scale)") +
  theme_tpa()

save_chart(fig_013, "fig_013")
```

# Figure 14 - Trends in International Student Enrollment in STEM Fields in U.S. Higher Education, by Broad STEM Field (2009–2024)
```{r figure 014}
meta <- get_meta("fig_014")

df_014 <- read_fig("fig_014") %>%
  select(-`Non STEM`,-`Social Sciences`) %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Field", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  order_by_latest(Field, Count)

labels_014 <- last_by_group(df_014, Year, Field)

fig_014 <- ggplot(df_014, aes(Year, Count, color = Field, group = Field)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_014,
    mapping      = aes(label = paste0(Field, ": ", label_comma()(Count))),
    nudge_x      = 1,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_014$Year, pad_right = .5) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Enrolled students") +
  theme_tpa()

save_chart(fig_014, "fig_014")
```

# Figure 15 - Trends in Graduate Students in Science, by Year and by Citizenship Status (1997-2023)
```{r figure 015}
meta <- get_meta("fig_015")
df   <- read_citizenship_area("fig_015")
fig  <- plot_citizenship_area(df, meta, "Graduate students enrolled")
save_chart(fig, "fig_015")
```

# Figure 16 - Trends in Graduate Students Engineering, by Year and by Citizenship Status (1997-2023)
```{r figure 016}
meta <- get_meta("fig_016")
df   <- read_citizenship_area("fig_016")
fig  <- plot_citizenship_area(df, meta, "Graduate students enrolled")
save_chart(fig, "fig_016")
```

# Figure 17 - Trends in Graduate Students in Health, by Citizenship Status (1997-2023)
```{r figure 017}
meta <- get_meta("fig_017")
df   <- read_citizenship_area("fig_017")
fig  <- plot_citizenship_area(df, meta, "Graduate students enrolled")
save_chart(fig, "fig_017")
```

# Figure 18 - Trends in US Citizen Research Doctorate Recipients from U.S. Colleges and Universities, by Year and by Broad Science and Engineering Field (2013-2023)
```{r figure 018}
meta <- get_meta("fig_018")
df   <- read_country_lines("fig_018", group_col = "Field", value_col = "Count")
fig  <- plot_country_lines(df, meta, "Doctorate recipients",
                           group_col   = "Field",
                           color_scale = scale_color_fields(),
                           pad_right   = .6)
save_chart(fig, "fig_018")
```

# Figure 19 - Trends in Temporary Visa Holder Research Doctorate Recipients from U.S. Colleges and Universities, by Year and by Broad Science and Engineering Field (2013-2023)
```{r figure 019}
meta <- get_meta("fig_019")
df   <- read_country_lines("fig_019", group_col = "Field", value_col = "Count") %>%
  filter(!is.na(Year))
fig  <- plot_country_lines(df, meta, "Doctorate recipients",
                           group_col   = "Field",
                           color_scale = scale_color_fields(),
                           pad_right   = .6)
save_chart(fig, "fig_019")
```

# Figure 20 - International Postdoctoral Representation by Field, 1980–2023
```{r figure 020}
meta <- get_meta("fig_020")

df_020 <- read_fig("fig_020") %>%
  rename(Year = 1,
         Science     = 2,
         Engineering = 3,
         Health      = 4) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Field", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  order_by_latest(Field, Share)

labels_020 <- last_by_group(df_020, Year, Field)

fig_020 <- ggplot(df_020, aes(Year, Share, color = Field, group = Field)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_020,
    mapping      = aes(label = paste0(Field, ": ", sprintf("%.1f%%", Share))),
    nudge_x      = 0.9,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_020$Year, pad_right = .25) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 80),
                     breaks = seq(0, 80, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "International share of postdocs") +
  theme_tpa()

save_chart(fig_020, "fig_020")
```

# Figure 21 - Trends in Postdocs at Federally Funded Research and Development Centers, by Citizenship (2012-2023)
```{r figure 021}
meta <- get_meta("fig_021")

df_021 <- read_fig("fig_021") %>%
  rename(Year = 1,
         `U.S. citizens and permanent residents` = 2,
         `Temporary visa holders`                = 3) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Status", values_to = "Count") %>%
  filter(!is.na(Year), !is.na(Count)) %>%
  order_by_latest(Status, Count)

labels_021 <- df_021 %>%
  nudge_by_series(Status,
                  above  = "Temporary visa holders",
                  amount = 120)

fig_021 <- ggplot(df_021, aes(Year, Count, color = Status, group = Status)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_label_repel_tpa(
    data         = labels_021,
    mapping      = aes(label = label_comma()(Count)),
    nudge_y      = labels_021$nudge_y,
    direction    = "y",
    with_segment = FALSE
  ) +
  scale_x_years(df_021$Year, by = 1, pad_right = PAD_RIGHT_TIGHT) +
  scale_y_continuous(labels = label_comma(),
                     limits = c(0, 2500),
                     breaks = seq(0, 2500, 500),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = citizenship_colors_alt) +
  labs_meta(meta, y = "Postdoctoral researchers") +
  theme_tpa()

save_chart(fig_021, "fig_021")
```

# Figure 22 - Trends in International Scholars Working in the United States, by Year (1954/55-2023/24)
```{r figure 022}
meta <- get_meta("fig_022")
df   <- read_discrete_bar("fig_022")
fig  <- plot_discrete_bar(df, meta, "International scholars",
                          label_fn = label_comma())
save_chart(fig, "fig_022")
```

# Figure 23 - Trends in International Scholars, by Year and by World Region of Origin (2000/01-2023/24)
```{r figure 023}
meta <- get_meta("fig_023")
df   <- read_country_lines("fig_023", group_col = "Region", value_col = "Count") %>%
  filter(Region != "Stateless")
fig  <- plot_country_lines(df, meta, "International scholars",
                           group_col = "Region",
                           pad_right = .6)
save_chart(fig, "fig_023")
```

# Figure 24 - Distribution of Major Field of Specialization of International Scholars Working in the United States (2013/2014—2023/24)
```{r figure 024}
meta <- get_meta("fig_024")

fields_keep <- c("Agriculture", "Engineering", "Health professions",
                 "Math and computer science", "Physical and life sciences",
                 "Social sciences", "Non-STEM")

df_024 <- read_fig("fig_024") %>%
  rename(Year = 1) %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Field", values_to = "Count") %>%
  filter(!is.na(Year), !is.na(Count), Field %in% fields_keep) %>%
  mutate(Field = factor(Field, levels = rev(fields_keep)))

fig_024 <- ggplot(df_024, aes(Year, Count, fill = Field)) +
  geom_col(width = 0.7, alpha = ALPHA_COL) +
  scale_x_years(df_024$Year, by = 1) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = stem_gradient_colors) +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs_meta(meta, y = "International scholars") +
  theme_tpa()

save_chart(fig_024, "fig_024")
```

# Figure 25 - Distribution of Citizenship Status in Demographic Characteristics for U.S. Population Ages 16–75, by U.S. STEM Labor Force Status and by Citizenship Status (2022)
```{r figure 025}
meta <- get_meta("fig_025")

status_order <- c(
  "Employed in the U.S. Labor Force in a STEM Occupation Directed Related to Science and Engineering",
  "Employed in the U.S. Labor Force in a STEM Occupation Indirectly Related to Science and Engineering",
  "Employed in the U.S. Labor Force in a STEM Occupation with a STEM middle skill",
  "Employed in the U.S. Labor Force in a non-STEM Occupation",
  "Unemployed in the U.S. Labor Force",
  "Not in the U.S. labor force",
  "Total"
)

df_025 <- read_fig("fig_025") %>%
  mutate(
    total_n                              = US_citizen + TPV,
    `U.S. citizen or permanent resident` = US_citizen / total_n,
    `Temporary visa holder`              = TPV / total_n
  ) %>%
  select(Category,
         `U.S. citizen or permanent resident`,
         `Temporary visa holder`) %>%
  pivot_longer(-Category, names_to = "Citizenship", values_to = "Share") %>%
  mutate(
    Category    = factor(Category, levels = rev(status_order)),
    Citizenship = factor(Citizenship,
                         levels = c("U.S. citizen or permanent resident",
                                    "Temporary visa holder"))
  ) %>%
  arrange(Category, Citizenship) %>%
  group_by(Category) %>%
  mutate(
    x_end   = cumsum(Share),
    x_start = x_end - Share,
    x_mid   = (x_start + x_end) / 2
  ) %>%
  ungroup()

palette_025 <- c(
  "U.S. citizen or permanent resident" = tpa_colors[2],
  "Temporary visa holder"              = tpa_colors[1]
)

bar_height <- 0.35

fig_025 <- ggplot(df_025) +
  geom_rect(aes(
    xmin = x_start,
    xmax = x_end,
    ymin = as.numeric(Category) - bar_height,
    ymax = as.numeric(Category) + bar_height,
    fill = Citizenship
  )) +
  geom_text(
    data     = filter(df_025, Citizenship == "Temporary visa holder"),
    aes(x = x_mid, y = as.numeric(Category),
        label = label_percent(accuracy = 1)(Share)),
    color    = "white",
    fontface = "bold",
    family   = FONT_FAMILY,
    size     = DATA_LABEL_SIZE / .pt
  ) +
  scale_x_continuous(
    labels = label_percent(accuracy = 1),
    breaks = seq(0.84, 1, 0.02),
    limits = c(0.84, 1),
    oob    = scales::oob_keep,
    expand = expansion(mult = c(0, 0))
  ) +
  scale_y_continuous(
    breaks = seq_along(levels(df_025$Category)),
    labels = label_wrap_gen(40)(levels(df_025$Category)),
    expand = expansion(add = c(0.5, 0.5))
  ) +
  scale_fill_manual(values = palette_025) +
  labs_meta(meta) +
  theme_horizontal_bar()

save_chart(fig_025, "fig_025")
```

# Figure 26 - Temporary Visa Holder Share of Employment by Detailed STEM Occupation, 2023
```{r figure 026}
meta <- get_meta("fig_026")

df_026 <- read_fig("fig_026") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Occupation", values_to = "Rate") %>%
  filter(!is.na(Rate)) %>%
  mutate(Rate = Rate * 100) %>%
  order_by_latest(Occupation, Rate)

labels_026 <- last_by_group(df_026, Year, Occupation) %>%
  mutate(label = paste0(str_wrap(Occupation, 24), ": ", fmt_pct_1(Rate)))

fig_026 <- ggplot(df_026, aes(Year, Rate, color = Occupation, group = Occupation)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_026,
    mapping      = aes(label = label),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    lineheight   = 0.85,
    with_segment = TRUE
  ) +
  scale_x_years(df_026$Year, by = 2, pad_right = PAD_RIGHT_XWIDE) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 20),
                     breaks = seq(0, 20, 5),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Conversion rate") +
  theme_tpa()

save_chart(fig_026, "fig_026")
```

# Figure 27 - Employment in STEM occupations by degree level, us citizens college graduates
```{r figure 027}
meta <- get_meta("fig_027")

level_order <- c("Doctorates", "Professional", "Masters", "Bachelors")

df_027 <- read_fig("fig_027") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Level", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share = Share * 100,
    Level = str_to_title(Level),
    Level = factor(Level, levels = level_order)
  )

labels_027 <- last_by_group(df_027, Year, Level)

fig_027 <- ggplot(df_027, aes(Year, Share, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_027,
    mapping      = aes(label = paste0(Level, ": ", fmt_pct_1(Share))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_027$Year, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(20, 60),
                     breaks = seq(0, 70, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = degree_employment_colors) +
  guides(color = "none") +
  labs_meta(meta, y = "Share employed in STEM") +
  theme_tpa()

save_chart(fig_027, "fig_027")
```

# Figure 28 - Employment in STEM occupations by degree level, foreign born college graduates
```{r figure 028}
meta <- get_meta("fig_028")

level_order <- c("Doctorates", "Professional", "Masters", "Bachelors")

df_028 <- read_fig("fig_028") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Level", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share = Share * 100,
    Level = str_to_title(Level),
    Level = factor(Level, levels = level_order)
  )

labels_028 <- last_by_group(df_028, Year, Level)

fig_028 <- ggplot(df_028, aes(Year, Share, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_028,
    mapping      = aes(label = paste0(Level, ": ", fmt_pct_1(Share))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_028$Year, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(20, 80),
                     breaks = seq(0, 80, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = degree_employment_colors) +
  guides(color = "none") +
  labs_meta(meta, y = "Share employed in STEM") +
  theme_tpa()

save_chart(fig_028, "fig_028")
```

# Figure 29 - STEM Degree-to-STEM job Conversion Rates (2017-2023)
```{r figure 029}
meta <- get_meta("fig_029")

df_029 <- read_fig("fig_029") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Level", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share = Share * 100,
    Level = case_when(
      str_detect(Level, regex("bach", ignore_case = TRUE)) ~ "Bachelors",
      str_detect(Level, regex("mast", ignore_case = TRUE)) ~ "Masters",
      str_detect(Level, regex("doct", ignore_case = TRUE)) ~ "Doctorate"
    ),
    Level = factor(Level, levels = c("Bachelors", "Masters", "Doctorate"))
  )

fig_029 <- ggplot(df_029, aes(factor(Year), Share, fill = Level)) +
  geom_col_grouped() +
  geom_text(aes(label = fmt_pct_1(Share)),
            position = pos_dodge_grouped(),
            vjust = -0.6,
            size = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family = FONT_FAMILY,
            color = "grey25") +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 60),
                     breaks = seq(0, 60, 10),
                     expand = EXPAND_TIGHT_TOP) +
  scale_fill_levels() +
  labs_meta(meta, y = "Share employed in STEM") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_029, "fig_029")
```

# Figure 30 - Top 15 Employers with NAICS Code 54 H-1B Visa Approvals
```{r figure 030}
# ---- shared fig_030 prep ----
# Full firm-level H-1B approvals (NAICS 54). Computes shares against
# the annual Grand Total row, excludes the partial 2026 column.
fig030_shares <- function() {
  raw <- read_fig("fig_030")
  names(raw) <- trimws(names(raw))

  total_row <- raw %>% filter(trimws(Company) == "Grand Total")
  totals <- total_row %>%
    select(-Company, -`Grand Total`) %>%
    pivot_longer(everything(), names_to = "Year", values_to = "Total") %>%
    mutate(Year = as.integer(Year), Total = as.numeric(Total))

  raw %>%
    filter(!trimws(Company) %in% c("Grand Total")) %>%
    mutate(Company = trimws(Company)) %>%
    select(-`Grand Total`) %>%
    pivot_longer(-Company, names_to = "Year", values_to = "Count") %>%
    mutate(Year = as.integer(Year),
           Count = as.numeric(replace_na(Count, 0))) %>%
    filter(Year != 2026) %>%                     # drop partial year
    left_join(totals, by = "Year") %>%
    mutate(Share = Count / Total * 100)
}

meta <- get_meta("fig_030")

short_names <- c(
  "COGNIZANT TECHNOLOGY SOLUTIONS US CORP"      = "Cognizant",
  "TATA CONSULTANCY SERVICES LIMITED"           = "Tata",
  "INFOSYS LIMITED"                             = "Infosys",
  "GOOGLE INC"                                  = "Google",
  "Deloitte and Subsidiaries"                   = "Deloitte",
  "WIPRO LIMITED"                               = "WIPRO",
  "ERNST & YOUNG LLP"                           = "Ernst & Young",
  "TECH MAHINDRA AMERICAS INC"                  = "Tech Mahindra",
  "HCL Technologies Limited and Subsidiaries"   = "HCL",
  "CAPGEMINI AMERICA INC"                       = "Capgemini",
  "LTIMINDTREE LIMITED"                         = "LTIMindtree",
  "IBM and subsidiaries"                        = "IBM",
  "LARSEN & TOUBRO INFOTECH LIMITED"            = "Larsen & Toubro"
)

shares <- fig030_shares()

# rank union firms by their max share across the two years, so the
# biggest bars (Cognizant's 2017, Google's 2025) sit on the left
df_bar <- shares %>%
  filter(Year %in% c(2017, 2025), Company %in% names(short_names)) %>%
  mutate(Company = recode(Company, !!!short_names),
         Year = factor(Year))

bar_order <- df_bar %>%
  group_by(Company) %>% summarise(m = max(Share)) %>%
  arrange(desc(m)) %>% pull(Company)

df_bar <- df_bar %>% mutate(Company = factor(Company, levels = bar_order))

fig_030a <- ggplot(df_bar, aes(Company, Share, fill = Year)) +
  geom_col(position = position_dodge(width = BAR_WIDTH),
           width = BAR_WIDTH, alpha = ALPHA_COL) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 24), breaks = seq(0, 20, 5),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = c("2017" = tpa_colors[2], "2025" = tpa_colors[1])) +
  labs_meta(meta, y = "Share of H-1B approvals (NAICS 54)") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

save_chart(fig_030a, "fig_030")
```

# Figure 31 - The Evolving Founder Demographics of the US-Based Forbes AI 50 Companies (2019–2025)
```{r figure 031}
meta <- get_meta("fig_031")

df_031 <- read_fig("fig_031") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Composition", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share       = Share * 100,
    Composition = case_when(
      Composition == "all us"       ~ "All U.S.",
      Composition == "all foreign"  ~ "All foreign",
      Composition == "some foreign" ~ "Some foreign"
    )
  ) %>%
  order_by_latest(Composition, Share)

palette_031 <- c(
  "All U.S."     = tpa_colors[1],
  "All foreign"  = tpa_colors[2],
  "Some foreign" = tpa_colors[4]
)

labels_031 <- last_by_group(df_031, Year, Composition)

fig_031 <- ggplot(df_031, aes(Year, Share, color = Composition, group = Composition)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = POINT_SIZE) +
  geom_label_repel_tpa(
    data         = labels_031,
    mapping      = aes(label = paste0(Composition, ": ", fmt_pct_1(Share))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_031$Year, by = 1, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(20, 50),
                     breaks = seq(0, 50, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = palette_031) +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Forbes AI 50") +
  theme_tpa()

save_chart(fig_031, "fig_031")
```

# Figure 32 - Countries of Origin for Foreign Founders of U.S.-Based AI Companies Ranked in the Forbes AI5o (2019-2025)
```{r figure 032}
meta <- get_meta("fig_032")

df_032 <- read_fig("fig_032") %>%
  rename(Country = 1, Count = 2) %>%
  mutate(
    Count = as.numeric(Count),
    Country = case_when(
      Country == "the Netherlands"     ~ "Netherlands",
      Country == "United Arab Emirates" ~ "United Arab Emirates",
      Country == "Scotland"             ~ "United Kingdom",
      Country == "Hong Kong"            ~ "Hong Kong S.A.R.",
      TRUE                              ~ Country
    )
  ) %>%
  group_by(Country) %>%
  summarise(Count = sum(Count, na.rm = TRUE), .groups = "drop")

world_032 <- join_country_data(df_032)

fig_032 <- ggplot(world_032) +
  geom_sf(aes(fill = Count), color = "white", linewidth = 0.2) +
  geom_country_labels(world_032, value_col = "Count", min_value = 5) +
  scale_fill_gradient(
    low = TPA_RED_LIGHT,
    high = tpa_colors[1],
    na.value = "grey92",
    breaks = c(1, 20, 40, 60, 76),
    labels = label_comma(),
    name = "Founders"
  ) +
  coord_sf(crs = "+proj=robin", expand = FALSE) +
  labs_meta(meta) +
  theme_map()

save_chart(fig_032, "fig_032")
```

# Figure 33 - Founder Composition and Valuation of Forbes AI50 Startups
```{r figure 033}
# Figure 33 - Founder Composition and Valuation of Forbes AI50 Startups
fig033_data <- function() {
  raw <- read_fig("fig_033")
  names(raw) <- make.unique(names(raw))   # de-dupe the repeated headers
  foreign <- raw %>%
    transmute(Company,
              Valuation = as.numeric(`Pitchbook Valuation`),
              Origin = "Foreign-founded") %>%
    filter(!is.na(Valuation))
  domestic <- raw %>%
    transmute(Company,
              Valuation = as.numeric(`Pitchbook Valuation.1`),
              Origin = "Domestic-founded") %>%
    filter(!is.na(Valuation))
  bind_rows(foreign, domestic) %>%
    mutate(ValB = Valuation / 1e9)
}

meta <- get_meta("fig_033")

df_top <- fig033_data() %>%
  slice_max(ValB, n = 25) %>%
  mutate(Company = fct_reorder(Company, ValB))

fig_033 <- ggplot(df_top, aes(ValB, Company, color = Origin)) +
  geom_point(size = 3.2) +
  scale_x_log10(labels = label_dollar(suffix = "B", accuracy = 1),
                breaks = c(1, 3, 10, 30, 100, 300),
                expand = expansion(mult = c(0.04, 0.08))) +
  scale_color_manual(values = c("Foreign-founded"  = "#C46C5D",
                                "Domestic-founded" = "#A6C5DE")) +
  labs_meta(meta, y = NULL) +
  labs(x = "Valuation (log scale)") +
  theme_dotplot() +
  theme(
    panel.grid.major.y = element_line(color = "grey92", linewidth = 0.3),
    # theme_dotplot blanks the x-axis (value is normally on each dot);
    # this chart has no dot labels, so restore the axis and title it
    axis.text.x  = element_text(family = FONT_FAMILY, color = "grey25",
                                size = AXIS_SIZE, angle = 0, hjust = 0.5,
                                margin = margin(t = 4)),
    axis.ticks.x = element_line(color = "grey50", linewidth = 0.35),
    axis.line.x  = element_line(color = "grey50", linewidth = 0.4),
    axis.title.x = element_text(family = FONT_FAMILY, color = "grey25",
                                size = AXIS_SIZE, margin = margin(t = 8))
  )

save_chart(fig_033, "fig_033")
```

# Figure 34 - Geographic Affiliation Distribution of Research Paper Authors from Top AI Companies (2025)
```{r figure 034}
meta <- get_meta("fig_034")

company_order <- c("Alphabet","Anthropic", "OpenAI", "Alibaba", "DeepSeek", "Moonshot")
category_order <- c("Rest of World", "China", "United States")

df_034 <- read_fig("fig_034") %>%
  rename(Company = 1) %>%
  pivot_longer(-Company, names_to = "Affiliation", values_to = "Share") %>%
  mutate(
    Share = as.numeric(Share) * 100,
    Affiliation = str_remove(Affiliation, "^Current Affiliation - ?"),
    Affiliation = factor(Affiliation, levels = category_order),
    Company = factor(Company, levels = company_order)
  )

palette_034 <- c(
  "United States"      = tpa_colors[2],
  "China"              = tpa_colors[1],
  "Rest of World"      = tpa_colors[3]
)

fig_034 <- ggplot(df_034, aes(Share, Company, fill = Affiliation)) +
  geom_col(width = BAR_WIDTH_NARROW, alpha = ALPHA_COL) +
  geom_text(aes(label = fmt_pct_0(Share)),
            position = position_stack(vjust = 0.5),
            color = "white",
            fontface = "bold",
            family = FONT_FAMILY,
            size = DATA_LABEL_SIZE / .pt) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     breaks = seq(0, 100, 10),
                     limits = c(0, 101),
                     expand = expansion(mult = c(0, 0))) +
  scale_fill_manual(values = palette_034,
                    breaks = c("United States", "China", "Rest of World")) +
  labs_meta(meta, x = "Share of researchers") +
  theme_horizontal_bar()

save_chart(fig_034, "fig_034")
```

# Figure 35 - US PISA Scores Compared to China and OECD Average
```{r figure 035}
meta <- get_meta("fig_035")

subject_order <- c("Reading", "Science", "Math")

df_035 <- read_fig("fig_035") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Subject", values_to = "Score") %>%
  filter(!is.na(Score)) %>%
  mutate(Subject = factor(Subject, levels = subject_order))

palette_035 <- c(
  "Reading" = tpa_colors[1],   # red
  "Science" = tpa_colors[4],   # green
  "Math"    = tpa_colors[2]    # navy
)

fig_035 <- ggplot(df_035, aes(Year, Score, color = Subject, group = Subject)) +
  geom_hline(yintercept = 0, color = "grey50", linewidth = LINE_WIDTH_REF) +
  geom_trend() +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_text(aes(label = sprintf("%+d", Score)),
            vjust = -1.1,
            size = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_continuous(breaks = unique(df_035$Year),
                     expand = expansion(mult = c(0.03, 0.03))) +
  scale_y_continuous(limits = c(-20, 32),
                     breaks = seq(-20, 30, 5),
                     expand = expansion(mult = c(0.02, 0.05))) +
  scale_color_manual(values = palette_035) +
  labs_meta(meta, y = "Score change from PISA baseline") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_035, "fig_035")
```

# Figure 36 - K-12 Education Expenditure - % of GDP and per pupil
```{r figure 036}
meta <- get_meta("fig_036")

df_036 <- read_fig("fig_036") %>%
  rename(
    Year       = 1,
    GDP_share  = 2,
    Per_pupil  = 3
  ) %>%
  mutate(
    Year      = as.numeric(Year),
    GDP_share = as.numeric(GDP_share),
    Per_pupil = parse_number(as.character(Per_pupil))
  )

primary_range   <- c(12500, 16500)
secondary_range <- c(4.5, 5.5)

scale_factor <- diff(primary_range) / diff(secondary_range)
shift        <- primary_range[1] - secondary_range[1] * scale_factor

fig_036 <- ggplot(df_036, aes(Year)) +
  geom_col(aes(y = Per_pupil, fill = "Per-pupil expenditure"),
         width = 0.7, alpha = ALPHA_COL) +
  geom_line(aes(y = GDP_share * scale_factor + shift,
              color = "Education expenditure (% of GDP)"),
          linewidth = LINE_WIDTH, na.rm = TRUE) +
  geom_point(aes(y = GDP_share * scale_factor + shift,
                 color = "Education expenditure (% of GDP)"),
             size = 2, na.rm = TRUE) +
  scale_x_years(df_036$Year, by = 1) +
  scale_y_continuous(
    name = "Per-pupil expenditure",
    labels = label_dollar(),
    limits = primary_range,
    breaks = seq(12500, 16500, 500),
    expand = expansion(mult = c(0, 0)),
    oob = scales::oob_keep,
    sec.axis = sec_axis(
      transform = ~ (. - shift) / scale_factor,
      name = "Education expenditure (% of GDP)",
      labels = label_number(suffix = "%", accuracy = 0.1),
      breaks = seq(4.5, 5.5, 0.1)
    )
  ) +
  scale_fill_manual(name = NULL,
                    values = c("Per-pupil expenditure" = tpa_colors[4])) +
  scale_color_manual(name = NULL,
                     values = c("Education expenditure (% of GDP)" = tpa_colors[1])) +
  labs_meta(meta) +
  theme_dual_axis()

save_chart(fig_036, "fig_036")
```

# Figure 37 - US-trained Students – Undergraduate – STEM Major Persistence Rate – Three and Five-Year
```{r figure 037}
meta <- get_meta("fig_037")

category_order <- c("Never",
                    "Once by Year 3", "Once by Year 6",
                    "More than Once By Year 3", "More than Once By Year 6")

df_037 <- read_fig("fig_037") %>%
  rename(Survey = 1) %>%
  pivot_longer(-Survey, names_to = "Category", values_to = "Share") %>%
  mutate(
    Share = as.numeric(Share) * 100,
    Category = factor(Category, levels = category_order),
    Survey = factor(Survey, levels = c("2004/2009 Survey", "2012/2017 Survey"))
  )

palette_037 <- c(
  "2004/2009 Survey" = tpa_colors[2],   # navy
  "2012/2017 Survey" = tpa_colors[1]    # red
)

fig_037 <- ggplot(df_037, aes(Category, Share, fill = Survey)) +
  geom_col_grouped() +
  geom_text(aes(label = fmt_pct_1(Share)),
            position = pos_dodge_grouped(),
            vjust = -0.6,
            size = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family = FONT_FAMILY,
            color = "grey25") +
  scale_x_discrete(labels = function(x) str_wrap(x, 12)) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 70),
                     breaks = seq(0, 70, 10),
                     expand = EXPAND_TIGHT_TOP) +
  scale_fill_manual(values = palette_037) +
  labs_meta(meta, y = "Share of students") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_037, "fig_037")
```

# Figure 38 - STEM Graduation Outcomes by Initially Declared Major, All Cohorts
```{r figure 038}
meta <- get_meta("fig_038")

df_038 <- read_fig("fig_038") %>%
  rename(Cohort = 1) %>%
  mutate(Cohort = str_trim(Cohort)) %>%
  pivot_longer(-Cohort, names_to = "Outcome", values_to = "Share") %>%
  mutate(
    Share = as.numeric(Share) * 100,
    Cohort = factor(Cohort, levels = c("1990/1994", "1996/2001", "2004/2009", "2012/2017"))
  )

outcome_palette <- c(
  "Entered STEM, Graduated STEM"         = tpa_colors[2],   # navy
  "Entered STEM, Graduated non-STEM"     = tpa_colors[1],   # red
  "Entered non-STEM, Graduated STEM"     = tpa_colors[4],   # green
  "Entered non-STEM, Graduated non-STEM" = tpa_colors[5]    # purple
)

make_fig_038 <- function(outcome, y_limits, y_by) {
  df <- df_038 %>% filter(Outcome == outcome)
  series_color <- outcome_palette[[outcome]]
  
  ggplot(df, aes(Cohort, Share, group = 1)) +
    geom_trend(color = series_color) +
    geom_line(linewidth = LINE_WIDTH, color = series_color) +
    geom_point(size = 2, color = series_color) +
    geom_text(aes(label = fmt_pct_1(Share)),
              vjust = -1.1,
              size = DATA_LABEL_SIZE / .pt,
              fontface = "bold",
              family = FONT_FAMILY,
              color = series_color) +
    scale_y_continuous(labels = label_number(suffix = "%"),
                       limits = y_limits,
                       breaks = seq(y_limits[1], y_limits[2], y_by),
                       expand = expansion(mult = c(0.05, 0.10))) +
    labs(title = outcome,
         subtitle = NULL,
         caption = NULL,
         x = NULL, y = "Share of students") +
    theme_tpa() +
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5))
}

fig_038a <- make_fig_038("Entered STEM, Graduated STEM",
                         y_limits = c(50, 70), y_by = 2) +
  labs(title = "Entered STEM, Graduated STEM",
       subtitle = meta$subtitle,
       caption = meta$caption)
save_chart(fig_038a, "fig_038a")

fig_038b <- make_fig_038("Entered STEM, Graduated non-STEM",
                         y_limits = c(30, 50), y_by = 2) +
  labs(title = "Entered STEM, Graduated non-STEM",
       subtitle = meta$subtitle,
       caption = meta$caption)
save_chart(fig_038b, "fig_038b")

fig_038c <- make_fig_038("Entered non-STEM, Graduated STEM",
                         y_limits = c(0, 20), y_by = 2) +
  labs(title = "Entered non-STEM, Graduated STEM",
       subtitle = meta$subtitle,
       caption = meta$caption)
save_chart(fig_038c, "fig_038c")

fig_038d <- make_fig_038("Entered non-STEM, Graduated non-STEM",
                         y_limits = c(80, 100), y_by = 2) +
  labs(title = "Entered non-STEM, Graduated non-STEM",
       subtitle = meta$subtitle,
       caption = meta$caption)
save_chart(fig_038d, "fig_038d")
```

# Figure 39 - Trends in U.S. Students Studying Abroad (For Academic Credit), by Year (1989/90-2022/2023)
```{r figure 039}
meta <- get_meta("fig_039")
df   <- read_discrete_bar("fig_039")
fig  <- plot_discrete_bar(df, meta, "U.S. students studying abroad",
                          label_fn = label_comma())
save_chart(fig, "fig_039")
```

# Figure 40 - Distribution of Field of Study in U.S. Study Abroad Students (2000/01-2023/24)
```{r figure 040}
meta <- get_meta("fig_040")
df   <- read_country_lines("fig_040", group_col = "Field", value_col = "Share")
fig  <- plot_country_lines(df, meta, "Share of U.S. students abroad",
                           group_col = "Field",
                           value_col = "Share",
                           label_fmt = fmt_pct_1,
                           x_by      = 2,
                           pad_right = .6,
                           y_args    = list(
                             labels = label_number(suffix = "%"),
                             limits = c(0, 35),
                             breaks = seq(0, 35, 5),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_040")
```

# Figure 41 - Distribution of Host Regions of U.S. Students Studying Abroad (For Academic Credit), by Year and By World Region (2004/05-2022/23)
```{r figure 041}
meta <- get_meta("fig_041")

df_041 <- read_fig("fig_041") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Region", values_to = "Share") %>%
  filter(!is.na(Share), Region != "Antarctica") %>%
  order_by_total(Region, Share)

fig_041 <- ggplot(df_041, aes(Year, Share, fill = Region)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_041$Year, by = 2) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 10),
                     expand = expansion(mult = c(0, 0))) +
  scale_fill_stacked(n = 8) +
  labs_meta(meta, y = "Share of U.S. students abroad") +
  theme_tpa()

save_chart(fig_041, "fig_041")
```

# Figure 42 - Net flow of internationally mobile students (inbound - outbound) (UIS estimate)
```{r figure 042}
meta <- get_meta("fig_042")

df_042 <- read_fig("fig_042") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Flow") %>%
  filter(!is.na(Flow)) %>%
  mutate(Flow = Flow / 1e6) %>%
  order_by_latest(Country, Flow)

highlight_042 <- highlight_colors(
  df_042$Country,
  highlighted = c("United States of America", "China"),
  palette     = c(tpa_colors[2], tpa_colors[1])
)

labels_042 <- df_042 %>%
  filter(Country %in% c("United States of America", "China")) %>%
  group_by(Country) %>%
  slice_max(Year, n = 1) %>%
  ungroup() %>%
  mutate(label = paste0(
    if_else(Country == "United States of America", "United States", Country),
    ": ", sprintf("%.2fM", Flow)
  ))

fig_042 <- ggplot(df_042, aes(Year, Flow, color = Country, group = Country)) +
  geom_hline(yintercept = 0, color = "grey50", linewidth = LINE_WIDTH_REF) +
  geom_line(linewidth = LINE_WIDTH_DENSE) +
  geom_label_repel_tpa(
    data         = labels_042,
    mapping      = aes(label = label),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_042$Year, by = 2, pad_right = PAD_RIGHT_NARROW) +
  scale_y_continuous(labels = function(x) paste0(sprintf("%.1f", x), "M"),
                     expand = expansion(mult = c(0.05, 0.05))) +
  scale_color_manual(values = highlight_042) +
  guides(color = "none") +
  labs_meta(meta, y = "Net flow (millions of students)") +
  theme_tpa()

save_chart(fig_042, "fig_042")
```

# Figure 43 - US Universities in the Top 100 in Each STEM Field, Averaged (2014-2025)
```{r figure 043}
meta <- get_meta("fig_043")

df_043 <- read_fig("fig_043") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric))

primary_range   <- c(30, 45)
secondary_range <- c(30, 45)
scale_factor <- diff(primary_range) / diff(secondary_range)
shift        <- primary_range[1] - secondary_range[1] * scale_factor

fig_043 <- ggplot(df_043, aes(Year)) +
  geom_col(aes(y = `Avg Count`, fill = "Avg count of US universities in top 100"),
           width = BAR_WIDTH, alpha = ALPHA_COL) +
  geom_trend(mapping = aes(y = `Avg Count`), color = tpa_colors[1]) +
  geom_line(aes(y = `Avg Rank` * scale_factor + shift,
                color = "Avg rank of US universities in top 100"),
            linewidth = LINE_WIDTH) +
  geom_point(aes(y = `Avg Rank` * scale_factor + shift,
                 color = "Avg rank of US universities in top 100"),
             size = POINT_SIZE) +
  geom_trend(mapping = aes(y = `Avg Rank` * scale_factor + shift), color = tpa_colors[4]) +
  geom_text(aes(y = `Avg Count`, label = round(`Avg Count`)),
            vjust    = -0.6,
            color    = tpa_colors[1],
            size     = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family   = FONT_FAMILY) +
  geom_text(aes(y = `Avg Rank` * scale_factor + shift,
                label = sprintf("%.1f", `Avg Rank`)),
            vjust    = -1.1,
            color    = tpa_colors[4],
            size     = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family   = FONT_FAMILY) +
  scale_x_years(df_043$Year, by = 1) +
  scale_y_continuous(
    name   = "Average count in top 100",
    limits = primary_range,
    breaks = seq(30, 45, 2),
    expand = EXPAND_NONE,
    oob    = scales::oob_keep,
    sec.axis = sec_axis(
      transform = ~ (. - shift) / scale_factor,
      name      = "Average rank",
      breaks    = seq(30, 45, 2)
    )
  ) +
  scale_fill_manual(name = NULL,
                    values = c("Avg count of US universities in top 100" = tpa_colors[1])) +
  scale_color_manual(name = NULL,
                     values = c("Avg count of US universities in top 100" = tpa_colors[1],
                                "Avg rank of US universities in top 100"  = tpa_colors[4])) +
  guides(fill  = guide_legend(order = 1),
         color = guide_legend(order = 2)) +
  labs_meta(meta) +
  theme_dual_axis() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_043, "fig_043")
```

# Figure 44 - Fractional Shares of Top-Cited Emerging-Technology Publications: China–US Trajectories, 2015–2024
```{r figure 044}
meta <- get_meta("fig_044")

df_044 <- read_fig("fig_044") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Share") %>%
  mutate(
    Share   = Share * 100,
    Country = case_when(
      Country == "china" ~ "China",
      Country == "us"    ~ "United States"
    )
  )

fig_044 <- ggplot(df_044, aes(Year, Share, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_text(aes(label = fmt_pct_0(Share)),
            vjust       = -1.1,
            size        = DATA_LABEL_SIZE / .pt,
            fontface    = "bold",
            family      = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_years(df_044$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 25),
                     breaks = seq(0, 25, 5),
                     expand = EXPAND_LINE) +
  scale_color_china_us() +
  labs_meta(meta, y = "Fractional share of top-cited publications") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_044, "fig_044")
```

# Figure 45 - U.S. and Chinese authorship shares in top emerging technology publications, 2015–2025
```{r figure 045}
meta <- get_meta("fig_045")

df_045 <- read_fig("fig_045") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Share") %>%
  mutate(
    Share   = Share * 100,
    Country = case_when(
      Country == "pct_papers_with_us" ~ "United States",
      Country == "pct_papers_with_cn" ~ "China"
    )
  )

fig_045 <- ggplot(df_045, aes(Year, Share, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_text(aes(label = fmt_pct_1(Share)),
            vjust       = -1.1,
            size        = DATA_LABEL_SIZE / .pt,
            fontface    = "bold",
            family      = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_years(df_045$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(15, 35),
                     breaks = seq(15, 35, 2),
                     expand = EXPAND_LINE) +
  scale_color_china_us() +
  labs_meta(meta, y = "Share of top emerging-tech publications") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_045, "fig_045")
```

# Figure 46 - Top 1% Most-Cited Researchers – US-Affiliated trends
```{r figure 046}
meta <- get_meta("fig_046")

df_046 <- read_fig("fig_046") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric),
         Share = Share * 100)

primary_range   <- c(0, 3000)
secondary_range <- c(0, 60)
scale_factor <- diff(primary_range) / diff(secondary_range)
shift        <- primary_range[1] - secondary_range[1] * scale_factor

fig_046 <- ggplot(df_046, aes(Year)) +
  geom_col(aes(y = Count, fill = "Top 1% most-cited US-affiliated researchers"),
         width = 0.7, alpha = ALPHA_COL) +
  geom_line(aes(y = Share * scale_factor + shift, color = "Share of global top 1%"),
          linewidth = LINE_WIDTH) +
  geom_point(aes(y = Share * scale_factor + shift,
                 color = "Share of global top 1%"),
             size = 2) +
  scale_x_years(df_046$Year, by = 1) +
  scale_y_continuous(
    name = "US-affiliated researchers",
    labels = label_comma(),
    limits = primary_range,
    breaks = seq(0, 3000, 500),
    expand = EXPAND_TIGHT_TOP,
    sec.axis = sec_axis(
      transform = ~ (. - shift) / scale_factor,
      name = "Share of global top 1%",
      labels = label_number(suffix = "%"),
      breaks = seq(0, 60, 10)
    )
  ) +
  scale_fill_manual(name = NULL,
                    values = c("Top 1% most-cited US-affiliated researchers" = tpa_colors[2])) +
  scale_color_manual(name = NULL,
                     values = c("Share of global top 1%" = tpa_colors[1])) +
  labs_meta(meta) +
  theme_dual_axis() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_046, "fig_046")
```

# Figure 47 - Share of Authors of NeurIPS Oral Presentations by Primary Country of Affiliation (2013-2025)
```{r figure 047}
meta <- get_meta("fig_047")

df_047 <- read_fig("fig_047") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Region", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share  = Share * 100,
    Region = factor(Region, levels = c("United States", "Rest of the World", "China"))
  )

palette_047 <- c(
  china_us_colors,
  "Rest of the World" = "grey55"
)

fig_047 <- ggplot(df_047, aes(Year, Share, color = Region, group = Region)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_text(aes(label = fmt_pct_1(Share)),
            vjust       = -1.1,
            size        = DATA_LABEL_SIZE / .pt,
            fontface    = "bold",
            family      = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_years(df_047$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 90),
                     breaks = seq(0, 90, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = palette_047) +
  labs_meta(meta, y = "Share of NeurIPS oral presentations") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_047, "fig_047")
```

# Figure 48 - Distribution of Author Affiliations, by Year and by Country (By Conference)
```{r figure 048}
meta <- get_meta("fig_048")

conf_names <- c(
  acl          = "Association for Computational Linguistics (NLP) [ACL]",
  acml         = "Asian Conference on Machine Learning (ML) [ACML]",
  aistats      = "AI and Statistics (Stats / ML) [AISTATS]",
  coling       = "Computational Linguistics (NLP) [COLING]",
  colt         = "Learning Theory (Theoretical ML) [COLT]",
  corl         = "Robot Learning (Robotics / ML) [CORL]",
  cvpr         = "Computer Vision and Pattern Recognition (CV) [CVPR]",
  emnlp        = "Empirical Methods in NLP (NLP) [EMNLP]",
  iccv         = "Computer Vision (CV) [ICCV]",
  iclr         = "Learning Representations (ML) [ICLR]",
  icml         = "Machine Learning (ML) [ICML]",
  icra         = "Robotics and Automation (Robotics) [ICRA]",
  ijcai        = "Artificial Intelligence (AI) [IJCAI]",
  iros         = "Intelligent Robots and Systems (Robotics) [IROS]",
  naacl        = "North American ACL (NLP) [NAACL]",
  nips         = "Neural Information Processing Systems (ML / AI) [NIPS]",
  rss          = "Robotics: Science and Systems (Robotics) [RSS]",
  siggraphasia = "SIGGRAPH Asia (Graphics) [SIGGRAPHASIA]",
  uai          = "Uncertainty in AI (AI / Probabilistic ML) [UAI]",
  wacv         = "Applications of Computer Vision (CV) [WACV]"
)

df_048 <- read_fig("fig_048") %>%
  mutate(across(c(year, count, share), as.numeric)) %>%
  filter(!is.na(share), country %in% c("United States", "China")) %>%
  mutate(
    share        = share * 100,
    conf_full    = conf_names[conf_norm],
    conf_wrapped = str_wrap(conf_full, 38),
    country      = factor(country, levels = c("United States", "China"))
  ) %>%
  filter(!is.na(conf_full))

# --- Facet (all conferences in one grid) ---
fig_048 <- ggplot(df_048, aes(year, share, color = country, group = country)) +
  geom_line(linewidth = LINE_WIDTH_FACET) +
  facet_wrap(~ conf_wrapped, ncol = 3, scales = "free_x") +
  scale_x_continuous(breaks = function(lims) {
    seq(ceiling(lims[1]), floor(lims[2]),
        by = max(1, round((lims[2] - lims[1]) / 4)))
  }) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 20),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_china_us() +
  labs_meta(meta, y = "Share of author affiliations") +
  theme_facet()

save_chart(fig_048, "fig_048", size = "xlong")

# --- Individual chart per conference ---
make_fig_048 <- function(code) {
  df <- df_048 %>% filter(conf_norm == code)

  ggplot(df, aes(year, share, color = country, group = country)) +
    geom_line(linewidth = LINE_WIDTH) +
    geom_point(size = POINT_SIZE) +
    scale_x_continuous(breaks = unique(df$year)) +
    scale_y_continuous(labels = label_number(suffix = "%"),
                       limits = c(0, 100),
                       breaks = seq(0, 100, 20),
                       expand = EXPAND_BAR_TIGHT) +
    scale_color_china_us() +
    labs(title    = conf_names[[code]],
         subtitle = meta$subtitle,
         caption  = meta$caption,
         x = NULL, y = "Share of author affiliations") +
    theme_tpa()
}

for (code in names(conf_names)) {
  if (!code %in% df_048$conf_norm) next
  fig <- make_fig_048(code)
  save_chart(fig, paste0("fig_048_", code))
  assign(paste0("fig_048_", code), fig, envir = .GlobalEnv)
}
```

# Figure 49 - Rolling Average of US Recipients of Top Awards in STEM Fields (2000-2024)
```{r figure 049}
meta <- get_meta("fig_049")

short_names <- c(
  "10-Year Rolling Average of US Affiliated Scientists Who Won A Nobel Prize in STEM" = "Nobel Prize - US Affiliated (10yr)",
  "10-Year Rolling Average of US Born Scientists Who Won A Nobel Prize in STEM"       = "Nobel Prize - US Born (10yr)",
  "10-Year Rolling Average of US Born Scientists Who Won A Turing Award"              = "Turing Award - US Born (10yr)",
  "10-Year Rolling Average of US Affiliated Scientists Who Won A Turing Award"        = "Turing Award - US Affiliated (10yr)",
  "20-Year Rolling Average of US Affiliated Scientists Who Won A Fields Medal"        = "Fields Medal - US Affiliated (20yr)"
)

df_049 <- read_fig("fig_049") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Award", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Award = recode(Award, !!!short_names)) %>%
  order_by_latest(Award, Count)

labels_049 <- last_by_group(df_049, Year, Award)

fig_049 <- ggplot(df_049, aes(Year, Count, color = Award, group = Award)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_049,
    mapping      = aes(label = paste0(Award, ": ", Count)),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_049$Year, by = 2, pad_right = PAD_RIGHT_XWIDE) +
  scale_y_continuous(limits = c(0, 60),
                     breaks = seq(0, 60, 10),
                     expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Rolling average of recipients") +
  theme_tpa()

save_chart(fig_049, "fig_049")
```

# Figure 50 - Distribution of Citizenship Status of U.S. Affiliated Nobel Laureates (1900-2025)
```{r figure 050}
meta <- get_meta("fig_050")

df_050 <- read_fig("fig_050") %>%
  rename(Status = 1) %>%
  pivot_longer(c(chemistry, medicine, physics),
               names_to = "Prize", values_to = "Count") %>%
  group_by(Status) %>%
  summarise(Count = sum(Count, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Status = factor(Status, levels = c("Born Citizen", "Immigrant")),
    Share  = Count / sum(Count) * 100
  ) %>%
  arrange(Status)

palette_050 <- c(
  "Born Citizen" = tpa_colors[2],
  "Immigrant"    = tpa_colors[1]
)

fig_050 <- ggplot(df_050, aes(x = Share, y = "Nobel laureates", fill = Status)) +
  geom_col(width = BAR_WIDTH_SINGLE, color = "white", linewidth = 0.5) +
  geom_text(
    data = df_050 %>% filter(Share >= 5),
    aes(label = paste0(Status, ": ", fmt_pct_1(Share))),
    position = position_stack(vjust = 0.5),
    color = "white", fontface = "bold",
    family = FONT_FAMILY, size = DATA_LABEL_SIZE / .pt
  ) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     breaks = seq(0, 100, 10),
                     limits = c(0, 100),
                     expand = expansion(mult = c(0, 0))) +
  scale_fill_manual(values = palette_050,
                    breaks = c("Born Citizen", "Immigrant")) +
  guides(fill = "none") +
  labs_meta(meta, x = "Share of U.S.-affiliated Nobel laureates") +
  theme_horizontal_bar() +
  theme(axis.text.y = element_blank())

save_chart(fig_050, "fig_050")
```

# Figure 51 - Distribution of Country of Origin of U.S. Affiliated Immigrant Nobel Laureates (1900-2025)
```{r figure 051}
meta <- get_meta("fig_051")

df_051 <- read_fig("fig_051") %>%
  rename(Country = 1, Count = 2) %>%
  mutate(
    Count   = as.numeric(Count),
    Country = case_when(
      Country == "the Netherlands" ~ "Netherlands",
      Country == "Czech Republic"  ~ "Czech Republic",
      Country == "South Korea"     ~ "Republic of Korea",
      TRUE                         ~ Country
    )
  ) %>%
  group_by(Country) %>%
  summarise(Count = sum(Count, na.rm = TRUE), .groups = "drop")

world_051 <- join_country_data(df_051)

fig_051 <- ggplot(world_051) +
  geom_sf(aes(fill = Count), color = "white", linewidth = 0.2) +
  geom_country_labels(world_051, value_col = "Count", min_value = 3) +
  scale_fill_gradient(
    low      = TPA_RED_LIGHT,
    high     = tpa_colors[1],
    na.value = "grey92",
    trans    = "sqrt",
    breaks   = c(1, 3, 6, 10, 15),
    labels   = label_comma(),
    name     = "Immigrant laureates"
  ) +
  coord_sf(crs = "+proj=robin", expand = FALSE) +
  labs_meta(meta) +
  theme_map()

save_chart(fig_051, "fig_051")
```

# Figure 52 - United States - Composition and Mobility of Researchers Contributing to Company-Affiliated AI Papers (2025)
```{r figure 052}
meta <- get_meta("fig_052")

category_order <- c(
  "Purely Domestic",
  "Started Domestic, Trained Abroad, Returned",
  "Started Abroad, Came to the US, Stayed",
  "Started Domestic, Trained Abroad, Stayed Abroad",
  "Started Abroad, Came to the US, Left",
  "Purely Abroad"
)

palette_052 <- mobility_colors_base
names(palette_052)[names(palette_052) == "Inbound, Stayed"] <- "Started Abroad, Came to the US, Stayed"
names(palette_052)[names(palette_052) == "Inbound, Left"]   <- "Started Abroad, Came to the US, Left"

df_052 <- read_fig("fig_052") %>%
  rename(Category = 1, Count = 2) %>%
  mutate(
    Count    = as.numeric(Count),
    Category = factor(Category, levels = rev(category_order)),
    Share    = Count / sum(Count) * 100
  ) %>%
  arrange(Category)

fig_052 <- ggplot(df_052, aes(x = Share, y = "Researchers", fill = Category)) +
  geom_col(width = BAR_WIDTH_SINGLE, color = "white", linewidth = 0.5) +
  geom_text(
    data     = df_052 %>% filter(Share >= 5),
    aes(label = fmt_pct_0(Share)),
    position = position_stack(vjust = 0.5),
    color    = "white",
    fontface = "bold",
    family   = FONT_FAMILY,
    size     = DATA_LABEL_SIZE / .pt
  ) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     breaks = seq(0, 100, 10),
                     limits = c(0, 100),
                     expand = expansion(mult = c(0, 0))) +
  scale_fill_manual(values = palette_052, breaks = category_order) +
  guides(fill = guide_legend(ncol = 2, byrow = TRUE)) +
  labs_meta(meta, x = "Share of U.S.-affiliated AI researchers") +
  theme_horizontal_bar() +
  theme(axis.text.y = element_blank())

save_chart(fig_052, "fig_052")
```

# Figure 53 - China - Composition and Mobility of Researchers Contributing to Company-Affiliated AI Papers (2025)
```{r figure 053}
meta <- get_meta("fig_053")

category_order <- c(
  "Purely Domestic",
  "Started Domestic, Trained Abroad, Returned",
  "Started Abroad, Came to China, Stayed",
  "Started Domestic, Trained Abroad, Stayed Abroad",
  "Started Abroad, Came to China, Left",
  "Purely Abroad"
)

palette_053 <- mobility_colors_base
names(palette_053)[names(palette_053) == "Inbound, Stayed"] <- "Started Abroad, Came to China, Stayed"
names(palette_053)[names(palette_053) == "Inbound, Left"]   <- "Started Abroad, Came to China, Left"

df_053 <- read_fig("fig_053") %>%
  rename(Category = 1, Count = 2) %>%
  mutate(
    Count    = as.numeric(Count),
    Category = factor(Category, levels = rev(category_order)),
    Share    = Count / sum(Count) * 100
  ) %>%
  arrange(Category)

fig_053 <- ggplot(df_053, aes(x = Share, y = "Researchers", fill = Category)) +
  geom_col(width = BAR_WIDTH_SINGLE, color = "white", linewidth = 0.5) +
  geom_text(
    data     = df_053 %>% filter(Share >= 5),
    aes(label = fmt_pct_0(Share)),
    position = position_stack(vjust = 0.5),
    color    = "white",
    fontface = "bold",
    family   = FONT_FAMILY,
    size     = DATA_LABEL_SIZE / .pt
  ) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     breaks = seq(0, 100, 10),
                     limits = c(0, 100),
                     expand = expansion(mult = c(0, 0))) +
  scale_fill_manual(values = palette_053, breaks = category_order) +
  guides(fill = guide_legend(ncol = 2, byrow = TRUE)) +
  labs_meta(meta, x = "Share of China-affiliated AI researchers") +
  theme_horizontal_bar() +
  theme(axis.text.y = element_blank())

save_chart(fig_053, "fig_053")
```

# Figure 54 - Short-term Impact Indicator - Distribution of 2-Year Mean Citedness by Company
```{r figure 054}
df_authors <- read_boxlike_authors()

meta    <- get_meta("fig_054")
fig_054 <- plot_boxlike_fig(df_authors, "2yr_mean_citedness",
                             x_label = "2-year mean citedness") +
  labs(title = meta$title, subtitle = meta$subtitle, caption = meta$caption)
save_chart(fig_054, "fig_054")
```

# Figure 55 - Lifetime Reach Indicator - Distribution of Cited by Count by Company
```{r figure 055}
meta    <- get_meta("fig_055")
fig_055 <- plot_boxlike_fig(df_authors, "cited_by_count",
                             x_label = "Cited by count") +
  labs(title = meta$title, subtitle = meta$subtitle, caption = meta$caption)
save_chart(fig_055, "fig_055")
```

# Figure 56 - Balanced Productivity & Impact Indicator - Distribution of h-index by Company
```{r figure 056}
meta    <- get_meta("fig_056")
fig_056 <- plot_boxlike_fig(df_authors, "h_index",
                             x_label = "h-index") +
  labs(title = meta$title, subtitle = meta$subtitle, caption = meta$caption)
save_chart(fig_056, "fig_056")
```

# Figure 57 - Reasonably Cited Works Indicator - Distribution of i10-index by Company
```{r figure 057}
meta    <- get_meta("fig_057")
fig_057 <- plot_boxlike_fig(df_authors, "i10_index",
                             x_label = "i10-index") +
  labs(title = meta$title, subtitle = meta$subtitle, caption = meta$caption)
save_chart(fig_057, "fig_057")
```

# Figure 58 - Output Volume Indicator - Distribution of Works Count by Company
```{r figure 058}
meta    <- get_meta("fig_058")
fig_058 <- plot_boxlike_fig(df_authors, "works_count",
                             x_label = "Works count") +
  labs(title = meta$title, subtitle = meta$subtitle, caption = meta$caption)
save_chart(fig_058, "fig_058")
```

# Figure 59 - Patents Granted in Biotechnologies by Country Office (Top 10)
```{r figure 059}
meta <- get_meta("fig_059")
df   <- read_patents("fig_059")
fig  <- plot_patents(df, meta, "Patents granted (log scale)")
save_chart(fig, "fig_059")
```

# Figure 60 - Patents Granted in Semiconductor Technologies by Country Office (Top 10)
```{r figure 060}
meta <- get_meta("fig_060")
df   <- read_patents("fig_060")
fig  <- plot_patents(df, meta, "Patents granted (log scale)")
save_chart(fig, "fig_060")
```

# Figure 61 - Patents Granted in Computer Technologies by Country Office (Top 10)
```{r figure 061}
meta <- get_meta("fig_061")
df   <- read_patents("fig_061")
fig  <- plot_patents(df, meta, "Patents granted (log scale)")
save_chart(fig, "fig_061")
```

# Figure 62 - Manufacturing Value Added in USD Trillion Dollars, 2010 - 2024
```{r figure 062}
meta <- get_meta("fig_062")
df   <- read_country_lines("fig_062", group_col = "Region", value_col = "Value") %>%
  mutate(Value = Value / 1e12)
fig  <- plot_country_lines(df, meta, "Manufacturing value added",
                           group_col = "Region",
                           value_col = "Value",
                           label_fmt = function(x) paste0("$", sprintf("%.1f", x), "T"),
                           x_by      = 1,
                           pad_right = PAD_RIGHT_STANDARD,
                           y_args    = list(
                             labels = function(x) paste0("$", x, "T"),
                             limits = c(0, 6),
                             breaks = seq(0, 6, 1),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_062")
```

# Figure 63 - Gross domestic expenditures on R&D, by selected region, country, or economy:
```{r figure 063}
meta <- get_meta("fig_063")
df   <- read_country_lines("fig_063", group_col = "Region", value_col = "Value") %>%
  mutate(Value = Value / 1000)
fig  <- plot_country_lines(df, meta, "R&D expenditure (USD billions, PPP)",
                           group_col = "Region",
                           value_col = "Value",
                           label_fmt = function(x) paste0("$", sprintf("%.0f", x), "B"),
                           y_args    = list(
                             labels = function(x) paste0("$", x, "B"),
                             limits = c(0, 1000),
                             breaks = seq(0, 1000, 100),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_063")
```

# Figure 64 - R&D Intensity in Critical Technology Sectors by Country
```{r figure 064}
meta <- get_meta("fig_064")
df   <- read_country_lines("fig_064", group_col = "Country", value_col = "Share") %>%
  mutate(Share = Share * 100)
fig  <- plot_country_lines(df, meta, "R&D intensity (% of GDP)",
                           value_col = "Share",
                           label_fmt = fmt_pct_1,
                           pad_right = PAD_RIGHT_NARROW,
                           y_args    = list(
                             labels = label_number(suffix = "%"),
                             limits = c(0, 16),
                             breaks = seq(0, 16, 2),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_064")
```

# Figure 65 - International PhD Recipients – Intention to Stay
```{r figure 065}
meta <- get_meta("fig_065")

df_065 <- read_fig("fig_065") %>%
  rename(Year = 1, Share = 2) %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric),
         Share = Share * 100)

fig_065 <- ggplot(df_065, aes(Year, Share)) +
  geom_col(fill = tpa_colors[2], width = 0.7, alpha = ALPHA_COL) +
  geom_text(aes(label = fmt_pct_0(Share)),
            vjust = -0.5,
            color = tpa_colors[2],
            size = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family = FONT_FAMILY) +
  scale_x_years(df_065$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(60, 80),
                     breaks = seq(60, 80, 2),
                     expand = EXPAND_TIGHT_TOP,
                     oob = scales::oob_keep) +
  coord_cartesian(ylim = c(60, 80)) +
  labs_meta(meta, y = "Intention to stay in the United States") +
  theme_tpa()

save_chart(fig_065, "fig_065")
```

# Figure 66 - Share of ‘Staying’ Responses on Intention to Stay After Receipt of Doctorate Among Temporary Visa Holder Recipients, by World Region
```{r figure 066}
meta <- get_meta("fig_066")
df   <- read_country_lines("fig_066", group_col = "Region", value_col = "Share") %>%
  filter(Region != "Region and country or economy unknown") %>%
  mutate(Share = Share * 100)
fig  <- plot_country_lines(df, meta, "Stay rate after doctorate",
                           group_col = "Region",
                           value_col = "Share",
                           label_fmt = fmt_pct_0,
                           pad_right = PAD_RIGHT_STANDARD,
                           y_args    = list(
                             labels = label_number(suffix = "%"),
                             limits = c(40, 90),
                             breaks = seq(40, 90, 10),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_066")
```

# Figure 67 - International STEM PhD Recipients – Stay Rates
```{r figure 067}
meta <- get_meta("fig_067")

df_067 <- read_fig("fig_067") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Rate", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share = Share * 100,
    Rate  = factor(Rate, levels = c("5-year stay rate", "10-year stay rate"))
  )

palette_067 <- c(
  "5-year stay rate"  = tpa_colors[2],   # navy
  "10-year stay rate" = tpa_colors[1]    # red
)

fig_067 <- ggplot(df_067, aes(Year, Share, color = Rate, group = Rate)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_point(size = 2) +
  geom_text(aes(label = fmt_pct_1(Share)),
            vjust = -1.1,
            size = DATA_LABEL_SIZE / .pt,
            fontface = "bold",
            family = FONT_FAMILY,
            show.legend = FALSE) +
  scale_x_years(df_067$Year, by = 2) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(50, 75),
                     breaks = seq(50, 75, 5),
                     expand = expansion(mult = c(0, 0.05))) +
  scale_color_manual(values = palette_067) +
  labs_meta(meta, y = "Stay rate") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_067, "fig_067")
```

# Figure 68 - Distribution of Postgraduation Plans After Receipt of Doctorate Among Science and Engineering Research Doctorate Recipients, by Broad Major Field (2023)
```{r figure 068}
meta <- get_meta("fig_068")

field_order <- c(
  "Agricultural sciences and natural resources",
  "Biological and biomedical sciences",
  "Computer and information sciences",
  "Engineering",
  "Geosciences, atmospheric, and ocean sciences",
  "Health sciences",
  "Mathematics and statistics",
  "Multidisciplinary/ interdisciplinary sciences",
  "Physical sciences",
  "Psychology",
  "Social sciences",
  "Non-science and engineering"
)

df_068 <- read_fig("fig_068") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Field", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Share = Share * 100,
    Field = factor(Field, levels = field_order),
    Year  = factor(Year)
  )

palette_068 <- c(
  "2021" = tpa_colors[2],   # navy
  "2022" = tpa_colors[1],   # red
  "2023" = tpa_colors[4],   # green
  "2024" = tpa_colors[5]    # purple
)

fig_068 <- ggplot(df_068, aes(Field, Share, fill = Year)) +
  geom_col_grouped() +
  scale_x_discrete(labels = function(x) str_wrap(x, 15)) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 10),
                     expand = EXPAND_TIGHT_TOP) +
  scale_fill_manual(values = palette_068) +
  labs_meta(meta, y = "Plans for postdoc or employment in the U.S.") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = AXIS_SIZE - 2))

save_chart(fig_068, "fig_068", size = "long")
```

# Figure 69 - Trends in Distribution of Employment Sector of Doctorate Recipients with Definite Postgraduation Commitments for Non-postdoc Employment in the United States (1993-2023) - TVH Recipients
```{r figure 069}
meta <- get_meta("fig_069")
df   <- read_sector_employment("fig_069")
fig  <- plot_sector_employment(df, meta, "Share of TVH doctorate recipients",
                               y_limits = c(0, 80),
                               y_breaks = seq(0, 80, 10))
save_chart(fig, "fig_069")
```

# Figure 70 - Trends in Distribution of Employment Sector of Doctorate Recipients with Definite Postgraduation Commitments for Non-postdoc Employment in the United States (1993-2023) - US Recipients
```{r figure 070}
meta <- get_meta("fig_070")
df   <- read_sector_employment("fig_070")
fig  <- plot_sector_employment(df, meta, "Share of US doctorate recipients",
                               y_limits = c(0, 60),
                               y_breaks = seq(0, 60, 10))
save_chart(fig, "fig_070")
```

# Figure 71 - STEM OPT Approvals, Applications Received, Approval Rates
```{r figure 071}
meta <- get_meta("fig_071")

df_071 <- read_fig("fig_071") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric),
         `Approval Rate` = `Approval Rate` * 100)

df_071_bars <- df_071 %>%
  select(Year, Received, Approved) %>%
  pivot_longer(-Year, names_to = "Status", values_to = "Count") %>%
  mutate(Status = factor(Status, levels = c("Received", "Approved")))

primary_max   <- 20000
secondary_max <- 100
scale_factor <- primary_max / secondary_max

fig_071 <- ggplot() +
  geom_col(data = df_071_bars,
           aes(Year, Count, fill = Status),
           position = position_dodge(width = 0.8),
           width = 0.7, alpha = ALPHA_COL) +
  geom_line(data = df_071,
          aes(Year, `Approval Rate` * scale_factor, color = "Approval rate"),
          linewidth = LINE_WIDTH) +
  geom_point(data = df_071,
             aes(Year, `Approval Rate` * scale_factor,
                 color = "Approval rate"),
             size = 2) +
  scale_x_years(df_071$Year, by = 1) +
  scale_y_continuous(
    name = "Applications",
    labels = label_comma(),
    limits = c(0, primary_max),
    breaks = seq(0, primary_max, 2500),
    expand = EXPAND_TIGHT_TOP,
    sec.axis = sec_axis_scaled(scale_factor,
                               name = "Approval rate",
                               labels = label_number(suffix = "%"))
  ) +
  scale_fill_manual(name = NULL,
                    values = c("Received" = tpa_colors[2],
                               "Approved" = tpa_colors[1])) +
  scale_color_manual(name = NULL,
                     values = c("Approval rate" = tpa_colors[5])) +
  labs_meta(meta) +
  theme_dual_axis()

save_chart(fig_071, "fig_071")
```

# Figure 72 - Trends in H-1B approvals, by Application Type (2009-2025)
```{r figure 072}
meta <- get_meta("fig_072")

df_072 <- read_fig("fig_072") %>%
  filter(!is.na(Year)) %>%
  select(Year, `New Approved`, `Renewal Approved`) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Type", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Type = factor(Type, levels = c("Renewal Approved", "New Approved")))

palette_072 <- c(
  "New Approved"     = tpa_colors[1],
  "Renewal Approved" = tpa_colors[4]
)

fig_072 <- ggplot(df_072, aes(Year, Count, fill = Type)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_072$Year, by = 1) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = palette_072,
                    breaks = c("New Approved", "Renewal Approved")) +
  labs_meta(meta, y = "H-1B approvals") +
  theme_tpa()

save_chart(fig_072, "fig_072")
```

# Figure 73 - Share of H-1B Visa Denials Per Fiscal Year
```{r figure 073}
meta <- get_meta("fig_073")
df   <- read_hb_denials("fig_073")
fig  <- plot_hb_denials(df, meta, "H-1B denials")
save_chart(fig, "fig_073")
```

# Figure 74 - Trends in H-1B approvals for NAICS Code 54 - Professional, Scientific, and Technical Services, by Application Type (2009-2025)
```{r figure 074}
meta <- get_meta("fig_074")

df_074 <- read_fig("fig_074") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Type", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Type = factor(Type, levels = c("Renewal Approved", "New Approved")))

palette_074 <- c(
  "New Approved"     = tpa_colors[2],
  "Renewal Approved" = tpa_colors[1]
)

fig_074 <- ggplot(df_074, aes(Year, Count, fill = Type)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_074$Year, by = 1) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = palette_074,
                    breaks = c("New Approved", "Renewal Approved")) +
  labs_meta(meta, y = "H-1B approvals (NAICS 54)") +
  theme_tpa()

save_chart(fig_074, "fig_074")
```

# Figure 75 - Share of H-1B Visa Denials Per Fiscal Year for NAICS Code 54 - Professional, Scientific, and Technical Services
```{r figure 075}
meta <- get_meta("fig_075")
df   <- read_hb_denials("fig_075")
fig  <- plot_hb_denials(df, meta, "H-1B denials (NAICS 54)")
save_chart(fig, "fig_075")
```

# Figure 76 - Distribution of PERM Applications by Status (2008-2024)
```{r figure 076}
meta <- get_meta("fig_076")

df_076 <- read_fig("fig_076") %>%
  filter(!is.na(Year)) %>%
  select(Year, Certified = `Certified (Current + Expired)`, Denied) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Status", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Status = factor(Status, levels = c("Denied", "Certified")))

palette_076 <- c(
  "Certified" = tpa_colors[1],
  "Denied"    = tpa_colors[6]
)

fig_076 <- ggplot(df_076, aes(Year, Count, fill = Status)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_076$Year, by = 1) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = palette_076,
                    breaks = c("Certified", "Denied")) +
  labs_meta(meta, y = "PERM applications") +
  theme_tpa()

save_chart(fig_076, "fig_076")
```

# Figure 77 - Distribution of Country of Origin of Certified PERM Applications (2008-2024)
```{r figure 077}
meta <- get_meta("fig_077")

df_077 <- read_fig("fig_077") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Country = case_when(
    Country == "Republic of Korea" ~ "South Korea",
    Country == "Phillippines"      ~ "Philippines",
    TRUE                           ~ Country
  )) %>%
  order_by_latest(Country, Count)

labels_077 <- last_by_group(df_077, Year, Country)

palette_077 <- c(tpa_colors, "grey40")

fig_077 <- ggplot(df_077, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH_DENSE) +
  geom_label_repel_tpa(
    data         = labels_077,
    mapping      = aes(label = paste0(Country, ": ", label_comma()(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_077$Year, by = 2, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_log10(labels = label_comma(),
                breaks  = c(10, 100, 500, 1000, 5000, 10000, 50000),
                expand  = EXPAND_LINE) +
  scale_color_manual(values = palette_077) +
  guides(color = "none") +
  labs_meta(meta, y = "PERM certifications (log scale)") +
  theme_tpa()

save_chart(fig_077, "fig_077")
```

# Figure 78 - Trends in J-1 Visa Participation by Country (Top 10 overall from the last decade)
```{r figure 078}
meta <- get_meta("fig_078")

df_078 <- read_fig("fig_078") %>%
  filter(!is.na(Year)) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(Share = Share * 100) %>%
  order_by_latest(Country, Share)

labels_078 <- last_by_group(df_078, Year, Country)

palette_078 <- c(tpa_colors, "grey40", "grey60")

fig_078 <- ggplot(df_078, aes(Year, Share, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH_DENSE) +
  geom_label_repel_tpa(
    data         = labels_078,
    mapping      = aes(label = paste0(Country, ": ", fmt_pct_1(Share))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_078$Year, by = 1, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 12),
                     breaks = seq(0, 12, 2),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = palette_078) +
  guides(color = "none") +
  labs_meta(meta, y = "Share of J-1 participants") +
  theme_tpa()

save_chart(fig_078, "fig_078")
```

# Figure 79 - Immigrant vs Native-Born Workforce Participation Rate Gap, by Country (2024)
```{r figure 079}
meta <- get_meta("fig_079")

df_079 <- read_fig("fig_079") %>%
  rename(Gap = `Gap with the native-born`) %>%
  mutate(Gap = as.numeric(Gap),
         Country = fct_reorder(Country, Gap))

palette_079 <- highlight_colors(
  all_values  = levels(df_079$Country),
  highlighted = c("United States", "OECD average"),
  palette     = c(tpa_colors[1], tpa_colors[3]),   # red, gold
  default     = tpa_colors[2]                       # navy
)

fig_079 <- ggplot(df_079, aes(Gap, Country, fill = Country)) +
  geom_vline(xintercept = 0, color = "grey50", linewidth = LINE_WIDTH_REF) +
  geom_col(width = 0.75, alpha = ALPHA_COL) +
  geom_text(aes(label = sprintf("%.1f", Gap),
                hjust = if_else(Gap >= 0, -0.2, 1.2)),
            family = FONT_FAMILY,
            fontface = "bold",
            size = (DATA_LABEL_SIZE - 2) / .pt,
            color = "grey25") +
  scale_x_continuous(limits = c(-15, 20),
                     breaks = seq(-15, 20, 5),
                     expand = EXPAND_NONE) +
  scale_fill_manual(values = palette_079) +
  guides(fill = "none") +
  labs_meta(meta, x = "Percentage point gap with the native-born") +
  theme_horizontal_bar() +
  theme(axis.text.y = element_text(size = AXIS_SIZE - 2))

save_chart(fig_079, "fig_079", size = "long")
```

# Figure 80 - Gross Domestic Expenditure on R&D as a Share of GDP, by Selected Economy (1991-2023)
```{r figure 080}
meta <- get_meta("fig_080")
df   <- read_country_lines("fig_080", group_col = "Country", value_col = "Share")
fig  <- plot_country_lines(df, meta, "R&D as share of GDP",
                           value_col = "Share",
                           label_fmt = fmt_pct_1,
                           y_args    = list(
                             labels = label_number(suffix = "%"),
                             limits = c(0, 5.2),
                             breaks = seq(0, 5, 1),
                             expand = EXPAND_BAR_TIGHT
                           ))
save_chart(fig, "fig_080")
```

# Figure 81 - Trends in Share of International Student Enrollment in STEM Fields in U.S. Higher Education, by Selected Country (2009-2024)
```{r figure 081}
meta <- get_meta("fig_081")
df   <- read_country_lines("fig_081", group_col = "Country", value_col = "Share")
fig  <- plot_country_lines(df, meta, "STEM share of country's U.S. enrollment",
                           value_col = "Share",
                           label_fmt = fmt_pct_0,
                           y_args    = list(
                             labels = label_number(suffix = "%"),
                             limits = c(20, 90),
                             breaks = seq(20, 90, 10),
                             expand = EXPAND_LINE
                           ))
save_chart(fig, "fig_081")
```

# Figure 82 - Share of H-1B Approvals - Top 10 Companies by Count vs. All Other Companies (2009-2025)
```{r figure 082}
meta <- get_meta("fig_082")

df_082 <- read_fig("fig_082") %>%
  rename(Year = `Company Normalized`) %>%
  filter(!is.na(Year)) %>%
  mutate(Year = as.numeric(Year)) %>%
  select(Year,
         `Top 10 companies`    = `Top 10 Companies by Count`,
         `All other companies` = `All Other Companies`) %>%
  pivot_longer(-Year, names_to = "Group", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(Share = Share * 100,
         Group = factor(Group, levels = c("Top 10 companies",
                                          "All other companies")))

labels_082 <- fl_by_group(df_082, Year, Share, Group)

palette_082 <- c(
  "Top 10 companies"    = tpa_colors[2],
  "All other companies" = tpa_colors[6]
)

fig_082 <- ggplot(df_082, aes(Year, Share, color = Group, group = Group)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_082,
    mapping      = aes(label = fmt_pct_1(Share)),
    direction    = "y",
    with_segment = FALSE
  ) +
  scale_x_years(df_082$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 80),
                     breaks = seq(0, 80, 10),
                     expand = EXPAND_BAR_TIGHT) +
  scale_color_manual(values = palette_082) +
  labs_meta(meta, y = "Share of H-1B approvals") +
  theme_tpa()

save_chart(fig_082, "fig_082")
```

# Figure 83 - Year of Last Enrollment Among Students Who Did Not Complete a Degree, by Cohort
```{r figure 083}
meta <- get_meta("fig_083")

df_083 <- read_fig("fig_083") %>%
  rename(Cohort = Year) %>%
  select(-`Attained Degree by Final Survey Year`) %>%
  pivot_longer(-Cohort, names_to = "Category", values_to = "Pct") %>%
  filter(!is.na(Pct)) %>%
  mutate(
    Category = case_when(
      str_detect(Category, "year 1")         ~ "Year 1",
      str_detect(Category, "year 2")         ~ "Year 2",
      str_detect(Category, "year 3")         ~ "Year 3",
      str_detect(Category, "year 4")         ~ "Year 4",
      str_detect(Category, "year 5")         ~ "Year 5",
      str_detect(Category, "year 6")         ~ "Year 6",
      str_detect(Category, "still enrolled") ~ "Still enrolled"
    ),
    Category = factor(Category, levels = c(
      "Year 1", "Year 2", "Year 3", "Year 4",
      "Year 5", "Year 6", "Still enrolled"
    )),
    Cohort = factor(Cohort, levels = c("1996/2001", "2004/2009", "2012/2017"))
  )

palette_083 <- c(
  "1996/2001" = tpa_colors[2],   # navy
  "2004/2009" = tpa_colors[1],   # red
  "2012/2017" = tpa_colors[4]    # green
)

fig_083 <- ggplot(df_083, aes(Category, Pct, fill = Cohort)) +
  geom_col_grouped() +
  geom_text(aes(label = sprintf("%.1f", Pct)),
            position = pos_dodge_grouped(),
            vjust = -0.5,
            family = FONT_FAMILY,
            fontface = "bold",
            size = (DATA_LABEL_SIZE - 2) / .pt,
            color = "grey25") +
  scale_y_continuous(labels = label_number(suffix = "%"),
                   expand = EXPAND_BAR_XLARGE) +
  scale_fill_manual(values = palette_083) +
  labs_meta(meta, y = "Share of students") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_083, "fig_083")
```

# Figure 84 - Bachelor's Degree Attainment and Enrollment Status for Students Who Entered STEM, by Cohort
```{r figure 084}
meta <- get_meta("fig_084")

df_084 <- read_fig("fig_084") %>%
  rename(Cohort   = Year,
         Left     = `Left without return`,
         Attained = `Degree Attained, Or Still Enrolled by Last Survey Year`) %>%
  pivot_longer(-Cohort, names_to = "Status", values_to = "Pct") %>%
  filter(!is.na(Pct)) %>%
  mutate(
    Status = factor(Status,
                    levels = c("Left", "Attained"),
                    labels = c("Left without return",
                               "Degree attained or still enrolled")),
    Cohort = factor(Cohort,
                    levels = c("2012/2017", "2004/2009", "1996/2001", "1990/1994"))
  )

palette_084 <- c(
  "Left without return"               = tpa_colors[2],   # navy
  "Degree attained or still enrolled" = tpa_colors[1]    # red
)

fig_084 <- ggplot(df_084, aes(Pct, Cohort, fill = Status)) +
  geom_col(width = BAR_WIDTH_NARROW, alpha = ALPHA_COL) +
  geom_text(aes(label = fmt_pct_1(Pct)),
            position = position_stack(vjust = 0.5),
            color = "white", fontface = "bold",
            family = FONT_FAMILY, size = DATA_LABEL_SIZE / .pt) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 20),
                     expand = EXPAND_NONE) +
  scale_fill_manual(values = palette_084,
                    breaks = c("Left without return",
                               "Degree attained or still enrolled")) +
  labs_meta(meta, x = "Share of cohort") +
  theme_horizontal_bar()

save_chart(fig_084, "fig_084")
```

# Figure 85 - Participants in Optional Practical Training (OPT),OPT Participants (Overall and STEM)
```{r figure 085}
meta <- get_meta("fig_085")

df_085 <- read_fig("fig_085") %>%
  filter(!is.na(Year)) %>%
  rename(Share = `Share of All International Students`) %>%
  mutate(across(everything(), as.numeric))

scale_factor <- dual_axis_scale(
  primary_max   = 350000,
  secondary_max = 30
)

fig_085 <- ggplot(df_085, aes(Year)) +
  geom_col(aes(y = Count, fill = "Count"),
         width = 0.7, alpha = ALPHA_COL_LIGHT) +
  geom_line(aes(y = Share * scale_factor, color = "Share"),
          linewidth = LINE_WIDTH) +
  scale_x_years(df_085$Year) +
  scale_y_continuous(
    name = "Number of international students",
    labels = label_comma(),
    limits = c(0, 350000),
    expand = EXPAND_TIGHT_TOP,
    sec.axis = sec_axis_scaled(scale_factor,
                               name = "Share of all international students",
                               labels = label_number(suffix = "%"))
  ) +
  scale_fill_manual(name = NULL,
                    values = c("Count" = tpa_colors[2])) +
  scale_color_manual(name = NULL,
                     values = c("Share" = tpa_colors[1])) +
  labs_meta(meta) +
  theme_dual_axis()

save_chart(fig_085, "fig_085")
```

# Figure 86 - Top Computer Science University Rankings by CSRankings.com (2000 vs 2025)
```{r figure 086, fig.height=10}
meta <- get_meta("fig_086")

df_086 <- read_fig("fig_086") %>%
  mutate(
    rank_2000 = suppressWarnings(as.numeric(as.character(`2000`))),
    rank_2025 = suppressWarnings(as.numeric(as.character(`2025`))),
    delta     = rank_2000 - rank_2025,
    direction = case_when(
      is.na(rank_2000) ~ "New",
      delta > 0        ~ "Improved",
      delta < 0        ~ "Declined",
      TRUE             ~ "Unchanged"
    ),
    csv_order = row_number()
  ) %>%
  arrange(rank_2025, csv_order) %>%
  mutate(Institution = factor(Institution, levels = rev(Institution)))

df_arrows      <- df_086 %>% filter(!is.na(rank_2000))
df_points_only <- df_086 %>% filter(is.na(rank_2000))

palette_086 <- c(
  "Improved" = tpa_colors[4],   # green
  "Declined" = tpa_colors[1],   # red
  "New"      = "grey60"
)

fig_086 <- ggplot(df_086, aes(y = Institution)) +
  geom_segment(
    data = df_arrows,
    aes(x = rank_2000, xend = rank_2025,
        yend = Institution, color = direction),
    arrow = arrow(length = unit(0.18, "cm"), type = "closed"),
    linewidth = 0.7
  ) +
  geom_point(
    data = df_points_only,
    aes(x = rank_2025, color = direction),
    size = POINT_SIZE,
    show.legend = FALSE
  ) +
  # 2000 rank labels (arrow tail)
  geom_text(
    data = df_arrows %>% filter(direction == "Improved"),
    aes(x = rank_2000, label = rank_2000),
    hjust = 1.3,
    size = (DATA_LABEL_SIZE - 3) / .pt,
    family = FONT_FAMILY,
    color = "grey25"
  ) +
  geom_text(
    data = df_arrows %>% filter(direction == "Declined"),
    aes(x = rank_2000, label = rank_2000),
    hjust = -0.3,
    size = (DATA_LABEL_SIZE - 3) / .pt,
    family = FONT_FAMILY,
    color = "grey25"
  ) +
  # 2025 rank labels (arrow head)
  geom_text(
    data = df_arrows %>% filter(direction == "Improved"),
    aes(x = rank_2025, label = rank_2025),
    hjust = -0.3,
    size = (DATA_LABEL_SIZE - 3) / .pt,
    family = FONT_FAMILY,
    color = "grey25"
  ) +
  geom_text(
    data = df_arrows %>% filter(direction == "Declined"),
    aes(x = rank_2025, label = rank_2025),
    hjust = 1.3,
    size = (DATA_LABEL_SIZE - 3) / .pt,
    family = FONT_FAMILY,
    color = "grey25"
  ) +
  # Delta labels on the far right
  geom_text(
    data = df_arrows,
    aes(x = -8, label = sprintf("%+d", delta), color = direction),
    hjust = 0,
    fontface = "bold",
    size = (DATA_LABEL_SIZE - 2) / .pt,
    family = FONT_FAMILY,
    show.legend = FALSE
  ) +
  scale_x_reverse(
    breaks = seq(0, 160, 20),
    limits = c(165, -18),
    expand = EXPAND_NONE
  ) +
  scale_color_manual(
    values = palette_086,
    breaks = c("Improved", "Declined"),
    labels = c("Improved ranking", "Declined ranking")
  ) +
  guides(color = guide_legend(override.aes = list(linewidth = 1.2))) +
  labs_meta(meta, x = "Rank") +
  theme_horizontal_bar() +
  theme(
    axis.text.y = element_text(size = AXIS_SIZE - 2),
    legend.position = "bottom"
  )

save_chart(fig_086, "fig_086", size = "long")
```

# Figure 87 - Trends in H-1B Denials, by Application Type (2009-2025)
```{r figure 087}
meta <- get_meta("fig_087")
df   <- read_hb_denials("fig_087")
fig  <- plot_hb_denials(df, meta, "H-1B denials")
save_chart(fig, "fig_087")
```

# Figure 88 - Trends in H-1B Denials for NAICS Code 54 - Professional, Scientific, and Technical Services, by Application Type (2009-2025)
```{r figure 088}
meta <- get_meta("fig_088")
df   <- read_hb_denials("fig_088")
fig  <- plot_hb_denials(df, meta, "H-1B denials (NAICS 54)")
save_chart(fig, "fig_088")
```

# Figure 89 - Trends in Science and Engineering Research Doctorate Recipients from U.S. Colleges and Universities, by Year and by Sex (1993-2023)
```{r figure 089}
meta <- get_meta("fig_089")

df_089 <- read_fig("fig_089") %>%
  filter(!is.na(Year)) %>%
  select(Year, Male, Female) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Sex", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  mutate(Sex = factor(Sex, levels = c("Male", "Female"))) %>%
  order_by_latest(Sex, Count)

palette_089 <- c("Male" = tpa_colors[2], "Female" = tpa_colors[1])

fig <- plot_country_lines(df_089, meta, "Doctorate recipients",
                          group_col   = "Sex",
                          value_col   = "Count",
                          label_fmt   = label_comma(),
                          pad_right   = PAD_RIGHT_NARROW,
                          color_scale = scale_color_manual(values = palette_089))
save_chart(fig, "fig_089")
```

# Figure 90 - Trends in Science and Engineering Research Doctorate Recipients from U.S. Colleges and Universities, by Year and by Citizenship Status (1978-2023)
```{r figure 090}
meta <- get_meta("fig_090")

df_090 <- read_fig("fig_090") %>%
  filter(!is.na(Year)) %>%
  rename(`U.S. citizens and permanent residents` = `U.S. citizen or permanent resident`,
         `Temporary visa holders`                = `Temporary visa holder`,
         `Unknown citizenship`                   = `Unknown citizenship`) %>%
  mutate(across(everything(), as.numeric)) %>%
  pivot_longer(-Year, names_to = "Status", values_to = "Count") %>%
  filter(!is.na(Count)) %>%
  order_by_total(Status, Count)

palette_090 <- c(
  "U.S. citizens and permanent residents" = tpa_colors[1],
  "Temporary visa holders"                = tpa_colors[4],
  "Unknown citizenship"                   = tpa_colors[8]
)

fig_090 <- ggplot(df_090, aes(Year, Count, fill = Status)) +
  geom_area(alpha = ALPHA_AREA) +
  scale_x_years(df_090$Year) +
  scale_y_continuous(labels = label_comma(),
                     expand = EXPAND_BAR) +
  scale_fill_manual(values = palette_090) +
  labs_meta(meta, y = "Doctorate recipients") +
  theme_tpa()

save_chart(fig_090, "fig_090")
```

# Figure 91 - Share of Degree Completions by U.S. Nonresidents, by Field - Bachelors (2003-2023)
```{r figure 091}
meta <- get_meta("fig_091")
df   <- read_nonresident_field("fig_091")
fig  <- plot_nonresident_field(df, meta, "Nonresident share of bachelor's completions")
save_chart(fig, "fig_091")
```

# Figure 92 - Share of Degree Completions by U.S. Nonresidents, by Field - Masters (2003-2023)
```{r figure 092}
meta <- get_meta("fig_092")
df   <- read_nonresident_field("fig_092")
fig  <- plot_nonresident_field(df, meta, "Nonresident share of master's completions")
save_chart(fig, "fig_092")
```

# Figure 93 - Share of Degree Completions by U.S. Nonresidents, by Field - Doctoral (2003-2023)
```{r figure 093}
meta <- get_meta("fig_093")
df   <- read_nonresident_field("fig_093")
fig  <- plot_nonresident_field(df, meta, "Nonresident share of doctoral completions")
save_chart(fig, "fig_093")
```

# Figure 94 - Trends in International Student Doctorate Completions in STEM Fields in U.S. Higher Education, by Country (2009-2024)
```{r figure 094}
meta <- get_meta("fig_094")

df_094 <- read_fig("fig_094") %>%
  rename(Year = `Country or economy and field`) %>%
  mutate(across(-Year, as.character)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  mutate(
    Year  = as.numeric(Year),
    Count = suppressWarnings(as.numeric(Count))
  ) %>%
  filter(!is.na(Year), !is.na(Count), Count > 0) %>%
  order_by_latest(Country, Count)

labels_094 <- last_by_group(df_094, Year, Country)

fig_094 <- ggplot(df_094, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_094,
    mapping      = aes(label = paste0(Country, ": ", label_comma()(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_094$Year, by = 1, pad_right = PAD_RIGHT_STANDARD) +
  scale_y_log10(labels = label_comma(),
                breaks  = c(50, 100, 500, 1000, 2500, 5000),
                expand  = EXPAND_LINE) +
  scale_color_manual(values = c(tpa_colors, "grey40")) +
  guides(color = "none") +
  labs_meta(meta, y = "Doctorate completions (log scale)") +
  theme_tpa()

save_chart(fig_094, "fig_094")
```

# Figure 95 - Trends in Post-Doctoral Appointees in Science, by Citizenship Status (1997-2023)
```{r figure 095}
meta <- get_meta("fig_095")
df   <- read_citizenship_area("fig_095")
fig  <- plot_citizenship_area(df, meta, "Postdoctoral appointees")
save_chart(fig, "fig_095")
```

# Figure 96 - Trends in Post-Doctoral Appointees in Engineering, by Citizenship Status (1997-2023)
```{r figure 096}
meta <- get_meta("fig_096")
df   <- read_citizenship_area("fig_096")
fig  <- plot_citizenship_area(df, meta, "Postdoctoral appointees")
save_chart(fig, "fig_096")
```

# Figure 97 - Trends in Post-Doctoral Appointees in Health, by Citizenship Status (1997-2023)
```{r figure 097}
meta <- get_meta("fig_097")
df   <- read_citizenship_area("fig_097")
fig  <- plot_citizenship_area(df, meta, "Postdoctoral appointees")
save_chart(fig, "fig_097")
```

# Figure 98 - Trends in Doctoral Production by Degree Level
```{r figure 98}
meta <- get_meta("fig_098")

m1 <- function(x) sprintf("%.1fM", x / 1e6)

df_098 <- read_levels("fig_098", value_col = "Count",
                      levels_order = c("Bachelors", "Masters", "Doctorate"))

last_098  <- last_by_group(df_098, Year, Level)
first_098 <- df_098 %>% group_by(Level) %>% slice_min(Year, n = 1) %>% ungroup()

fig_098 <- ggplot(df_098, aes(Year, Count, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = last_098,
    mapping      = aes(label = paste0(Level, ": ", m1(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  geom_label_repel_tpa(
    data         = first_098,
    mapping      = aes(label = m1(Count)),
    nudge_x      = -0.5,
    hjust        = 1,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_continuous(
    breaks = seq(min(df_098$Year), max(df_098$Year), 1),
    expand = expansion(mult = c(0.05, PAD_RIGHT_NARROW))
  ) +
  scale_y_continuous(labels = m1, expand = EXPAND_LINE) +
  scale_color_levels() +
  guides(color = "none") +
  labs_meta(meta, y = "Degrees awarded") +
  theme_tpa()

save_chart(fig_098, "fig_098")
```

# Figure 99 - International Student Share of All Degree Completions
```{r figure 099}
meta <- get_meta("fig_099")
pct  <- label_percent(accuracy = 1)
df_099 <- read_levels(
  "fig_099",
  value_col    = "Share",
  levels_order = c("Bachelors", "Masters",
                   "All Doctorates (IPEDS)", "Research Doctorates (SED)")
) %>%
  filter(!is.na(Share))
last_099  <- last_by_group(df_099, Year, Level)
first_099 <- df_099 %>% group_by(Level) %>% slice_min(Year, n = 1) %>% ungroup()

fig_099 <- ggplot(df_099, aes(Year, Share, color = Level, group = Level)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = last_099,
    mapping      = aes(label = paste0(pct(Share), " - ", Level)),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  geom_label_repel_tpa(
    data         = first_099,
    mapping      = aes(label = pct(Share)),
    nudge_x      = -0.5,
    hjust        = 1,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_continuous(
    breaks = seq(min(df_099$Year), max(df_099$Year), 2),
    expand = expansion(mult = c(0.05, .50))
  ) +
  scale_y_continuous(labels = pct, expand = EXPAND_LINE_WIDE) +
  scale_color_levels() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of completions") +
  theme_tpa()
save_chart(fig_099, "fig_099")
```

# Figure 100 - Trends in Research Doctorate Recipients from U.S. Colleges and Universities, All Fields, by Year (1958-2023)
```{r figure 100}
meta <- get_meta("fig_100")

df_100 <- read_fig("fig_100") %>%
  mutate(
    across(everything(), as.numeric),
    stem_share = 100 * `Just S&E fields` / `Doctorate recipients (number)`
  )

labels_100 <- first_last_peak(
  df_100,
  Year,
  `Doctorate recipients (number)`
)

stem_labels <- bind_rows(
  df_100 %>% slice_min(Year, n = 1),
  df_100 %>% slice_max(stem_share, n = 1)
) %>%
  distinct(Year, .keep_all = TRUE)

fig_100 <- ggplot(df_100, aes(x = Year)) +

  # STEM area
  geom_ribbon(
    aes(
      ymin = 0,
      ymax = `Just S&E fields`
    ),
    fill = tpa_colors[2],
    alpha = 0.30
  ) +

  # Non-STEM area stacked above STEM
  geom_ribbon(
    aes(
      ymin = `Just S&E fields`,
      ymax = `Doctorate recipients (number)`
    ),
    fill = "grey80",
    alpha = 0.45
  ) +

  # Original line
  geom_line(
    aes(y = `Doctorate recipients (number)`),
    linewidth = LINE_WIDTH,
    color = tpa_colors[1]
  ) +

  # Total doctorate labels
  geom_label_repel_tpa(
    data = labels_100,
    mapping = aes(
      y = `Doctorate recipients (number)`,
      label = fmt_num_k(`Doctorate recipients (number)`)
    ),
    color = tpa_colors[1],
    nudge_y = 5000,
    with_segment = TRUE
  ) +

  # STEM share labels (first year + peak share year)
  geom_label_repel_tpa(
    data = stem_labels,
    mapping = aes(
      y = `Just S&E fields`,
      label = paste0(round(stem_share), "%")
    ),
    color = tpa_colors[2],
    nudge_y = -5000,
    with_segment = TRUE
  ) +

  scale_x_years(df_100$Year) +
  scale_y_continuous(
    labels = label_comma(),
    expand = EXPAND_LINE_TALL
  ) +

  labs_meta(meta, y = "Doctorate recipients") +
  theme_tpa()

save_chart(fig_100, "fig_100")
```

# Figure 101 - International Students as a Share of Total U.S. Higher Education Enrollment
```{r fig_101}
meta <- get_meta("fig_101")

df_101 <- read_fig("fig_009") %>%
  select(Year, value = "Share of Total US Enrollment") %>%        
  mutate(across(everything(), as.numeric),
         value = fill_gaps(Year, value))   

labels_101 <- first_last_peak(df_101, Year, value)

fig_101 <- ggplot(df_101, aes(Year, value)) +
  geom_line(linewidth = LINE_WIDTH, color = tpa_colors[1]) +
  geom_label_repel_tpa(
    data         = labels_101,
    mapping      = aes(label = label_percent(accuracy = 0.1)(value)), 
    color        = tpa_colors[1],
    nudge_y      = 0.004,                   
    with_segment = TRUE
  ) +
  scale_x_years(df_101$Year) +
  scale_y_continuous(labels = label_percent(accuracy = 1),  
                     expand = EXPAND_LINE_TALL) +
  labs_meta(meta, y = "Share of total US enrollment") +     
  theme_tpa()

save_chart(fig_101, "fig_101")
```

# Figure 102 - International Students in U.S. Higher Education, Count by Academic Level
```{r fig_102}
meta <- get_meta("fig_102")

df_102 <- read_fig("fig_102") %>%
  rename(
    `Graduate (unspecified)` = `Graduate - Unspecified`,
    `Non-degree`             = `Non-Degree`,
    OPT                      = `Optional Practical Training (OPT)`
  ) %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Level", values_to = "Count") %>%
  order_by_latest(Level, Count)

labels_102 <- last_by_group(df_102, Year, Level)

fig_102 <- ggplot(df_102, aes(Year, Count, color = Level, group = Level)) +
  geom_line(linewidth = 1) +
  geom_label_repel_tpa(
    data = labels_102,
    mapping = aes(label = paste0(Level, ": ", label_comma()(Count))),
    nudge_x = 0.5,
    hjust = 0,
    direction = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_102$Year, pad_right = 0.50) +
  scale_y_continuous(labels = label_comma(),
                     expand = expansion(mult = c(0.02, 0.05))) +
  scale_color_manual(values = acad_level_colors) +
  guides(color = "none") +
  labs_meta(meta, y = "International students enrolled") +
  theme_tpa()

save_chart(fig_102, "fig_102")
```

# Figure 103 - International Students in U.S. Higher Education, Share by Academic Level
```{r fig_103}
meta <- get_meta("fig_103")

df_103 <- read_fig("fig_103") %>%
  rename(
    `Graduate (unspecified)` = `Graduate - Unspecified`,
    `Non-degree`             = `Non-Degree`,
    OPT                      = `Optional Practical Training (OPT)`
  ) %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Level", values_to = "Count") %>%
  order_by_latest(Level, Count)

labels_103 <- last_by_group(df_103, Year, Level)

fig_103 <- ggplot(df_103, aes(Year, Count, color = Level, group = Level)) +
  geom_line(linewidth = 1) +
  geom_label_repel_tpa(
    data = labels_103,
    mapping = aes(label = paste0(Level, ": ", label_comma()(Count),"%")),
    nudge_x = 0.5,
    hjust = 0,
    direction = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_103$Year, pad_right = 0.50) +
  scale_y_continuous(labels = label_comma(),
                     expand = expansion(mult = c(0.02, 0.05))) +
  scale_color_manual(values = acad_level_colors) +
  guides(color = "none") +
  labs_meta(meta, y = "Share of International Enrollment (%)") +
  theme_tpa()

save_chart(fig_103, "fig_103")
```

# Figure 104 - International Students in U.S. Higher Education, Share by Academic Level
```{r fig_104}
meta <- get_meta("fig_104")

df_104 <- read_fig("fig_104")

fig_104 <- ggplot() +
  block_arrow_layers(df_104, Category, Change,
                     fills = arrow_fill,
                     divider_after = 1) +
  labs_meta(meta) +
  theme_arrows()

save_chart(fig_104, "fig_104", size = "standard")
```

# Figure 105 - Perspectives of Increases in International Enrollment
```{r fig_105}
meta <- get_meta("fig_105")

df_105 <- read_fig("fig_105") %>%
  rename(Reason = 1) %>%
  mutate(across(-Reason, as.numeric)) %>%
  pivot_longer(-Reason, names_to = "Cohort", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Cohort = factor(Cohort, levels = c("Fall 2018", "Fall 2021", "Fall 2025")),
    Reason = str_wrap(Reason, width = 50),                 # <- lower width = narrower text column
    Reason = factor(Reason, levels = rev(unique(Reason)))
  )

cohort_colors <- c(
  "Fall 2018" = tpa_colors[1],
  "Fall 2021" = tpa_colors[2],
  "Fall 2025" = tpa_colors[3]
)

# Spread crowded value labels horizontally; gap is in percentage points.
gap <- 4
labels_105 <- df_105 %>%
  group_by(Reason) %>%
  arrange(Share, .by_group = TRUE) %>%
  mutate(
    spread  = accumulate(Share, ~ max(.y, .x + gap)),
    label_x = spread - (mean(spread) - mean(Share))
  ) %>%
  ungroup()

fig_105 <- ggplot(df_105, aes(Share, Reason, color = Cohort)) +
  geom_point(size = 3.5) +
  geom_text(
    data = labels_105,
    aes(x = label_x, label = paste0(Share, "%")),
    nudge_y = -0.34,
    size = (DATA_LABEL_SIZE - 2) / .pt,
    fontface = "bold",
    family = FONT_FAMILY,
    show.legend = FALSE
  ) +
  scale_x_continuous(expand = expansion(mult = c(0.07, 0.07))) +
  scale_y_discrete(expand = expansion(add = c(0.8, 0.6))) +
  scale_color_manual(values = cohort_colors) +
  guides(color = guide_legend(override.aes = list(size = 3.5))) +
  coord_cartesian(clip = "off") +
  labs_meta(meta) +
  theme_dotplot()

save_chart(fig_105, "fig_105", size="standard")
```

# Figure 106 - Perspectives of Decreases in International Enrollment
```{r fig_106}
meta <- get_meta("fig_106")

df_106 <- read_fig("fig_106") %>%
  rename(Reason = 1) %>%
  mutate(across(-Reason, as.numeric)) %>%
  pivot_longer(-Reason, names_to = "Cohort", values_to = "Share") %>%
  filter(!is.na(Share)) %>%
  mutate(
    Cohort = factor(Cohort, levels = c("Fall 2018", "Fall 2021", "Fall 2025")),
    Reason = str_wrap(Reason, width = 50),                 # <- lower width = narrower text column
    Reason = factor(Reason, levels = rev(unique(Reason)))
  )

cohort_colors <- c(
  "Fall 2018" = tpa_colors[1],
  "Fall 2021" = tpa_colors[2],
  "Fall 2025" = tpa_colors[3]
)

# Spread crowded value labels horizontally; gap is in percentage points.
gap <- 4
labels_106 <- df_106 %>%
  group_by(Reason) %>%
  arrange(Share, .by_group = TRUE) %>%
  mutate(
    spread  = accumulate(Share, ~ max(.y, .x + gap)),
    label_x = spread - (mean(spread) - mean(Share))
  ) %>%
  ungroup()

fig_106 <- ggplot(df_106, aes(Share, Reason, color = Cohort)) +
  geom_point(size = 3.5) +
  geom_text(
    data = labels_106,
    aes(x = label_x, label = paste0(Share, "%")),
    nudge_y = -0.34,
    size = (DATA_LABEL_SIZE - 2) / .pt,
    fontface = "bold",
    family = FONT_FAMILY,
    show.legend = FALSE
  ) +
  scale_x_continuous(expand = expansion(mult = c(0.07, 0.07))) +
  scale_y_discrete(expand = expansion(add = c(0.8, 0.6))) +
  scale_color_manual(values = cohort_colors) +
  guides(color = guide_legend(override.aes = list(size = 3.5))) +
  coord_cartesian(clip = "off") +
  labs_meta(meta) +
  theme_dotplot()

save_chart(fig_106, "fig_106", size="standard")
```

# Figure 107 - Institutional Undergraduate and Graduate Recruitment Priorities, Fall 2025
```{r fig_107}
meta <- get_meta("fig_107")

panel_colors <- c(
  "Undergraduate" = tpa_colors[1],   # gold
  "Graduate"      = tpa_colors[2]     # teal (not in tpa_colors; swap for tpa_colors[2] navy for house palette)
)

track_max <- 1.0   # grey track length; nudge up toward ~1.1 if fills look too long

df_107 <- read_fig("fig_107") %>%
  transmute(
    Rank                  = as.integer(str_remove(Rank, "Rank ")),
    Undergraduate_Country = `Undergraduate Country`,
    Undergraduate_Value   = as.numeric(`Undergraduate Percent`),
    Graduate_Country      = `Graduate Country`,
    Graduate_Value        = as.numeric(`Graduate Percent`)
  ) %>%
  pivot_longer(-Rank, names_to = c("Panel", ".value"), names_sep = "_") %>%
  mutate(
    Panel   = factor(Panel, levels = c("Undergraduate", "Graduate")),
    Country = str_wrap(Country, width = 18),
    Country = reorder_within(Country, -Rank, Panel)   # rank 1 on top, per panel
  )

fig_107 <- ggplot(df_107, aes(y = Country)) +
  geom_col(aes(x = track_max), fill = "grey90", width = 0.65) +
  geom_col(aes(x = Value, fill = Panel), width = 0.65) +
  geom_text(aes(x = track_max, label = label_percent(accuracy = 1)(Value)),
            hjust = -0.25, fontface = "bold", color = "grey20",
            size = DATA_LABEL_SIZE / .pt, family = FONT_FAMILY) +
  facet_wrap(~ Panel, scales = "free_y") +
  scale_x_continuous(expand = expansion(mult = c(0, 0.14))) +
  scale_y_reordered() +
  scale_fill_manual(values = panel_colors) +
  coord_cartesian(clip = "off") +
  labs_meta(meta) +
  theme_bullet()

save_chart(fig_107, "fig_107")
```
# Figure 108 - Top 10 countries by international undergraduate enrollment (count)
```{r 108}
meta <- get_meta("fig_108")

df_108 <- read_fig("fig_108") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_108 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_108 <- df_108 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_108 <- last_by_group(df_108, Year, Country)

fig_108 <- ggplot(df_108, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_108,
    mapping      = aes(label = paste0(Country, ": ", label_comma()(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_108$Year, pad_right = .3) +
  scale_y_continuous(labels = label_comma(),
                breaks = c(1000, 5000, 10000, 50000, 100000, 250000),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Enrolled International Students") +
  theme_tpa()

save_chart(fig_108, "fig_108")
```

# Figure 109 - Top 10 countries by international undergraduate enrollment (share)
```{r 109}
meta <- get_meta("fig_109")

df_109 <- read_fig("fig_109") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_109 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_109 <- df_109 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_109 <- last_by_group(df_109, Year, Country)

fig_109 <- ggplot(df_109, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_109,
    mapping      = aes(label = paste0(Country, ": ", label_percent(accuracy = 0.1)(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_109$Year, pad_right = .3) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Enrolled International Students") +
  theme_tpa()

save_chart(fig_109, "fig_109")
```

# Figure 110 - Top 10 countries by international graduate enrollment (count)
```{r 110}
meta <- get_meta("fig_110")

df_110 <- read_fig("fig_110") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_110 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_110 <- df_110 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_110 <- last_by_group(df_110, Year, Country)

fig_110 <- ggplot(df_110, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_110,
    mapping      = aes(label = paste0(Country, ": ", label_comma()(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_110$Year, pad_right = .3) +
  scale_y_continuous(labels = label_comma(),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Enrolled International Students") +
  theme_tpa()

save_chart(fig_110, "fig_110")
```

# Figure 111 - Top 10 countries by international graduate enrollment (share)
```{r 111}
meta <- get_meta("fig_111")

df_111 <- read_fig("fig_111") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_111 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_111 <- df_111 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_111 <- last_by_group(df_111, Year, Country)

fig_111 <- ggplot(df_111, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_111,
    mapping      = aes(label = paste0(Country, ": ", label_percent(accuracy = 0.1)(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_111$Year, pad_right = .3) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Enrolled International Students") +
  theme_tpa()

save_chart(fig_111, "fig_111")
```

# Figure 112 - What Share of Each Country's International Students Are Enrolled in Engineering?
```{r fig_112}
meta <- get_meta("fig_112")

df_112 <- read_fig("fig_112") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_112 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_112 <- df_112 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_112 <- last_by_group(df_112, Year, Country)

fig_112 <- ggplot(df_112, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_112,
    mapping      = aes(label = paste0(Country, ": ", label_percent(accuracy = 0.1)(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_112$Year, pad_right = .3) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Enrolled International Students") +
  theme_tpa()

save_chart(fig_112, "fig_112")
```

# Figure 113 - What Share of Each Country's International Students Are Enrolled in Math and Computer Science?
```{r fig_113}
meta <- get_meta("fig_113")

df_113 <- read_fig("fig_113") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_113 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_113 <- df_113 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_113 <- last_by_group(df_113, Year, Country)

fig_113 <- ggplot(df_113, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_113,
    mapping      = aes(label = paste0(Country, ": ", label_percent(accuracy = 0.1)(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_113$Year, pad_right = .3) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Enrolled International Students") +
  theme_tpa()

save_chart(fig_113, "fig_113")
```

# Figure 114 - What Share of Each Country's International Students Are Enrolled in Physical and Life Sciences?
```{r fig_114}
meta <- get_meta("fig_114")

df_114 <- read_fig("fig_114") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "Count") %>%
  filter(!is.na(Count))

top_countries <- df_114 %>%
  filter(Year == max(Year)) %>%
  slice_max(Count, n = 8) %>%
  pull(Country)

df_114 <- df_114 %>%
  filter(Country %in% top_countries) %>%
  order_by_latest(Country, Count)

labels_114 <- last_by_group(df_114, Year, Country)

fig_114 <- ggplot(df_114, aes(Year, Count, color = Country, group = Country)) +
  geom_line(linewidth = LINE_WIDTH) +
  geom_label_repel_tpa(
    data         = labels_114,
    mapping      = aes(label = paste0(Country, ": ", label_percent(accuracy = 0.1)(Count))),
    nudge_x      = 0.5,
    hjust        = 0,
    direction    = "y",
    with_segment = TRUE
  ) +
  scale_x_years(df_114$Year, pad_right = .3) +
  scale_y_continuous(labels = label_percent(accuracy = 1),
                expand = EXPAND_LINE) +
  scale_color_tpa() +
  guides(color = "none") +
  labs_meta(meta, y = "Share of Enrolled International Students") +
  theme_tpa()

save_chart(fig_114, "fig_114")
```

# Figure 115 - Who Actually Works in STEM After Earning a STEM Degree?
```{r}
# shared prep -- combine US-born (fig_027) and foreign-born (fig_028)
# into one long frame with a Population column
prep_conversion <- function() {
  read_one <- function(name, pop) {
    read_fig(name) %>%
      mutate(across(-Year, as.numeric)) %>%
      pivot_longer(-Year, names_to = "Degree", values_to = "Rate") %>%
      mutate(Rate = Rate * 100, Population = pop)
  }

  bind_rows(
    read_one("fig_027", "U.S.-born"),
    read_one("fig_028", "Foreign-born")
  ) %>%
    mutate(
      Degree = recode(Degree,
        "bachelors"    = "Bachelors",
        "masters"      = "Masters",
        "doctorates"   = "Doctorates",
        "doctors"      = "Doctorates",
        "professional" = "Professional"),
      Degree = factor(Degree, levels = c("Doctorates", "Professional", "Masters", "Bachelors"))
    )
}

meta <- get_meta("fig_115")

first_yr <- 2003
last_yr  <- 2023

# long form: one row per Degree × Population × Year, with Year as a factor
# so it can drive the open/filled shape legend
df_db <- prep_conversion() %>%
  filter(Year %in% c(first_yr, last_yr)) %>%
  mutate(Year = factor(Year, levels = c(first_yr, last_yr)))

# wide, just for the connecting segments
df_seg <- df_db %>%
  select(Degree, Population, Year, Rate) %>%
  pivot_wider(names_from = Year, values_from = Rate, names_prefix = "Y")

fig_db <- ggplot(df_db, aes(y = Degree)) +
  geom_segment(data = df_seg,
               aes(x = Y2003, xend = Y2023, yend = Degree, color = Population),
               linewidth = 1.1, alpha = 0.55) +
  # both years drawn as shape 21; Year drives fill via the shape legend
  geom_point(aes(x = Rate, color = Population, shape = Year),
             fill = "white", stroke = 1.2, size = 3.8) +
  geom_point(data = filter(df_db, Year == last_yr),
             aes(x = Rate, color = Population, fill = Population),
             shape = 21, stroke = 0, size = 4) +
  scale_x_continuous(labels = label_number(suffix = "%"),
                     limits = c(20, 85), breaks = seq(20, 80, 10),
                     expand = expansion(mult = c(0.05, 0.10))) +
  scale_color_manual(values = c("U.S.-born"    = tpa_colors[2],
                                "Foreign-born" = tpa_colors[1])) +
  scale_fill_manual(values = c("U.S.-born"    = tpa_colors[2],
                               "Foreign-born" = tpa_colors[1]),
                    guide = "none") +
  scale_shape_manual(values = c("2003" = 21, "2023" = 19),
                     labels = c("2003" = "2003 (open)", "2023" = "2023 (filled)")) +
  guides(
    color = guide_legend(order = 1, override.aes = list(shape = 19, size = 4)),
    shape = guide_legend(order = 2,
                         override.aes = list(color = "grey40", fill = "white"))
  ) +
  labs_meta(meta, y = NULL) +
  theme_horizontal_bar()

save_chart(fig_db, "fig_115")
```

# Figure 116 - Top-10 H1B Visa Granted Firms Share Over time
```{r fig_116}
meta <- get_meta("fig_116")

# true top-10-by-year share: rank all firms each year, sum the top 10
df_116 <- fig030_shares() %>%
  group_by(Year) %>%
  slice_max(Count, n = 10) %>%
  summarise(value = sum(Share), .groups = "drop") %>%
  mutate(Year = as.numeric(Year))

labels <- first_last_peak(df_116, Year, value) %>%
  mutate(hj = dplyr::case_when(
    Year == min(df_116$Year) ~ -0.4,   # first point: label to the RIGHT (inward)
    Year == max(df_116$Year) ~  1.3,   # last point:  label to the LEFT (inward)
    TRUE                       ~  0.5    # peak: stays centered
  ))

fig_116 <- ggplot(df_116, aes(Year, value)) +
  geom_line(color = tpa_colors[1], linewidth = LINE_WIDTH) +
  geom_point(data = labels, color = tpa_colors[1], size = POINT_SIZE) +
  # peak label: house wrapper, centered above the point
  geom_text_tpa(data    = filter(labels, hj == .5),
                mapping = aes(label = sprintf("%.1f%%", value)),
                color   = tpa_colors[1],
                vjust   = 1.5) +
  # endpoint labels: nudged inward so they don't clip the panel edges
  geom_text(data    = filter(labels, hj != 0.5),
            mapping = aes(label = sprintf("%.1f%%", value), hjust = hj),
            color   = tpa_colors[1], fontface = "bold",
            family  = FONT_FAMILY, size = DATA_LABEL_SIZE / .pt) +
  scale_x_years(df_116$Year, by = 1) +
  scale_y_continuous(labels = label_number(suffix = "%"),
                     limits = c(50, 75),
                     breaks = seq(50, 75, 5),
                     expand = EXPAND_BAR_TALL) +
  labs_meta(meta, y = "Top 10 employers' share of approvals") +
  theme_tpa()

save_chart(fig_116, "fig_116")
```

# Figure 117 - How Does Founder Origin Vary Across AI Startup Valuations?
```{r fig_117}
meta <- get_meta("fig_117")

tier_levels  <- c("<$1B", "$1–10B", "$10–100B", "≥$100B")
origin_colors <- c("Foreign-founded"  = tpa_colors[1],
                   "Domestic-founded" = tpa_colors[2])

df_tier <- read_fig("fig_117") %>%
  rename(Origin = Binary) %>%
  mutate(Origin = recode(Origin,
    "Has All U.S. Born Founders"            = "Domestic-founded",
    "Has At Least One Foreign-Born Founder" = "Foreign-founded")) %>%
  pivot_longer(-Origin, names_to = "Tier", values_to = "n") %>%
  mutate(
    n    = replace_na(as.numeric(n), 0),          # blank ≥$100B cell -> 0
    Tier = factor(Tier, levels = tier_levels),
    Origin = factor(Origin, levels = c("Domestic-founded", "Foreign-founded"))
  )

fig_117 <- ggplot(df_tier, aes(Tier, n, fill = Origin)) +
  geom_col(position = position_dodge(width = BAR_WIDTH),
           width = BAR_WIDTH, alpha = ALPHA_COL) +
  geom_text(aes(label = n, color = Origin),
            position = position_dodge(width = BAR_WIDTH),
            vjust = -0.4, size = DATA_LABEL_SIZE / .pt,
            fontface = "bold", show.legend = FALSE) +
  scale_y_continuous(expand = EXPAND_BAR_TALL) +
  scale_fill_manual(values = origin_colors) +
  scale_color_manual(values = origin_colors) +
  labs_meta(meta, y = "Number of companies") +
  theme_tpa() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5))

save_chart(fig_117, "fig_117")
```

# Table 1 - US Universities Count in Top Universities Over Time
```{r table 1}
meta    <- get_meta("tab_001")
tab_001 <- build_ranking_table("tab_001", meta, integer_cols = TRUE)
tab_001
```

# Table 2 - US Universities Average Rank - All Fields Combined Trend
```{r table 002}
meta    <- get_meta("tab_002")
tab_002 <- build_ranking_table("tab_002", meta, integer_cols = FALSE)
tab_002
```

# Table 3 - Visa Processing Wait Time - EB1/EB2/EB3 - All Countries
```{r table 003}
meta    <- get_meta("tab_003")
tab_003 <- build_eb_table("tab_003", meta)
tab_003
```

# Table 4 - Visa Processing Wait Time - EB1/EB2/EB3 - China
```{r table 004}
meta    <- get_meta("tab_004")
tab_004 <- build_eb_table("tab_004", meta)
tab_004
```


# Table 5 - Visa Processing Wait Time - EB1/EB2/EB3 - India
```{r table 005}
meta    <- get_meta("tab_005")
tab_005 <- build_eb_table("tab_005", meta)
tab_005
```

# Table 6 - Change (1995-2024) in Int. Share of STEM Degrees Awarded by Field - Bachelors
```{r table 006}
meta_a <- get_meta("tab_006a")
meta_b <- get_meta("tab_006b")
meta_c <- get_meta("tab_006c")
meta_d  <- get_meta("tab_006d")

tab_006a <- build_change_table("tab_006a", meta_a)
tab_006b <- build_change_table("tab_006b", meta_b)
tab_006c <- build_change_table("tab_006c", meta_c)
tab_006d <- build_change_table_wide("tab_006d", meta_d)


tab_006a
tab_006b
tab_006c
tab_006d
```

# Table 7 - Change (1995-2024) in Int. Share of STEM Degrees Awarded by Field - Bachelors
```{r table 007}
meta_007 <- get_meta("tab_007")

tab_007 <- build_region_table(
  name = "tab_007",
  meta = meta_007
)

tab_007
```

# Table 8 - What Share of Each Country's International Students Are Enrolled in Key STEM Fields?
```{r table 008}
meta <- get_meta("tab_008")

field_files <- c(
  "Engineering"              = "fig_112",
  "Math & Computer Science"  = "fig_113",
  "Physical & Life Sciences" = "fig_114"
)

field_labels <- names(field_files)

read_field_long <- function(name) {
  read_fig(name) %>%
    mutate(across(-Year, ~ suppressWarnings(as.numeric(na_if(as.character(.x), "-"))))) %>%
    pivot_longer(-Year, names_to = "Country", values_to = "Share") %>%
    filter(!is.na(Share))
}

long_all <- imap(field_files, ~ read_field_long(.x) %>% mutate(Field = .y)) %>%
  bind_rows()

summ <- long_all %>%
  filter(Year %in% c(2009, 2024)) %>%
  mutate(point = if_else(Year == 2009, "First", "Last")) %>%
  select(Field, Country, point, Share) %>%
  pivot_wider(names_from = point, values_from = Share) %>%
  filter(!is.na(First), !is.na(Last)) %>%
  mutate(First = First * 100, Last = Last * 100,
         Change = (Last - First) / First * 100)

# keep only countries with both 2009 and 2024 values in all three fields
keep_countries <- summ %>% count(Country) %>% filter(n == 3) %>% pull(Country)
summ <- summ %>% filter(Country %in% keep_countries)

ord_cols <- as.vector(t(outer(field_labels, c("First", "Last", "Change"),
                              paste, sep = "_")))

country_order <- c(
  "China",
  "India",
  "South Korea",
  "Canada",
  "Japan",
  "Taiwan",
  "Saudi Arabia",
  "Mexico",
  "Vietnam",
  "Brazil",
  "Turkey/Türkiye",
  "Nigeria",
  "United Kingdom",
  "Germany",
  "Hong Kong",
  "Nepal",
  "Indonesia",
  "France",
  "Colombia",
  "Pakistan"
)

df_008 <- summ %>%
  pivot_wider(
    names_from  = Field,
    values_from = c(First, Last, Change),
    names_glue  = "{Field}_{.value}"
  ) %>%
  select(Country, all_of(ord_cols)) %>%
  arrange(match(Country, country_order)) %>%
  # ordered by mean field-share change; swap to e.g.
  # arrange(desc(`Engineering_Last`)) to order by 2024 engineering share
  mutate(.avg = rowMeans(across(ends_with("_Change")), na.rm = TRUE)) %>%
  select(-.avg)

build_field_share_table(df_008, "tab_008", meta, field_labels)
```

# Table 09 - International Share of U.S. Graduate Enrollment, by Field and Citizenship Status (1980–2024)
```{r tab_009}
meta <- get_meta("tab_009")

cite_files <- c(
  "Science"     = "fig_015",
  "Engineering" = "fig_016",
  "Health"      = "fig_017"
)

read_cite_long <- function(name) {
  read_fig(name) %>%
    mutate(across(-Year, ~ suppressWarnings(as.numeric(na_if(as.character(.x), "-"))))) %>%
    pivot_longer(-Year, names_to = "Group", values_to = "Count") %>%
    filter(!is.na(Count))
}

long_all <- imap(cite_files, ~ read_cite_long(.x) %>% mutate(Field = .y)) %>%
  bind_rows() %>%
  mutate(Group = recode(Group,
    "U.S. citizens and permanent residents" = "USC",
    "Temporary visa holders"                = "TVH"))

first_year <- min(long_all$Year, na.rm = TRUE)
last_year  <- max(long_all$Year, na.rm = TRUE)

# counts -> within-field citizenship share, per Field × Year
shares <- long_all %>%
  filter(Year %in% c(first_year, last_year)) %>%
  group_by(Field, Year) %>%
  mutate(Share = Count / sum(Count) * 100) %>%
  ungroup()

summ <- shares %>%
  mutate(point = if_else(Year == first_year, "First", "Last")) %>%
  select(Field, Group, point, Share) %>%
  pivot_wider(names_from = point, values_from = Share) %>%
  mutate(Change = (Last - First) / First * 100)   # relative change in share

ord_cols <- as.vector(t(outer(c("USC", "TVH"),
                              c("First", "Last", "Change"), paste, sep = "_")))

field_order <- c("Science", "Engineering", "Health")

df_009 <- summ %>%
  pivot_wider(
    names_from  = Group,
    values_from = c(First, Last, Change),
    names_glue  = "{Group}_{.value}"
  ) %>%
  select(Field, all_of(ord_cols)) %>%
  arrange(match(Field, field_order))

build_citizenship_table(df_009, "tab_009", meta,
                        first_year = first_year, last_year = last_year,
                        value_is_share = TRUE,
                        footnote = paste(
                          "Within-field citizenship share of U.S. graduate enrollment in",
                          "science, engineering, and health. Change is the relative change",
                          "in share between", first_year, "and", last_year, "."))
```

# Table 10 - Research Doctorate Recipients, by Field and Citizenship Status (2014–2024)
```{r table_010}
meta <- get_meta("tab_010")

phd_files <- c(
  "USC" = "fig_018",
  "TVH" = "fig_019"
)

read_phd_long <- function(name) {
  read_fig(name) %>%
    mutate(across(-Year, ~ suppressWarnings(as.numeric(na_if(as.character(.x), "-"))))) %>%
    pivot_longer(-Year, names_to = "Field", values_to = "Count") %>%
    filter(!is.na(Count)) %>%
    mutate(Field = recode(Field, "Social Science" = "Social Sciences"))
}

long_all <- imap(phd_files, ~ read_phd_long(.x) %>% mutate(Group = .y)) %>%
  bind_rows()

first_year <- min(long_all$Year, na.rm = TRUE)
last_year  <- max(long_all$Year, na.rm = TRUE)

summ <- long_all %>%
  filter(Year %in% c(first_year, last_year)) %>%
  mutate(point = if_else(Year == first_year, "First", "Last")) %>%
  select(Field, Group, point, Count) %>%
  pivot_wider(names_from = point, values_from = Count) %>%
  mutate(Change = (Last - First) / First * 100)

# wide counts: USC_First/Last/Change, TVH_First/Last/Change
counts_wide <- summ %>%
  pivot_wider(
    names_from  = Group,
    values_from = c(First, Last, Change),
    names_glue  = "{Group}_{.value}"
  )

# international share = TVH / (TVH + USC), per year, + relative change
df_010 <- counts_wide %>%
  mutate(
    SHR_First  = TVH_First / (TVH_First + USC_First) * 100,
    SHR_Last   = TVH_Last  / (TVH_Last  + USC_Last)  * 100,
    SHR_Change = (SHR_Last - SHR_First) / SHR_First * 100
  ) %>%
  select(Field,
         USC_First, USC_Last, USC_Change,
         TVH_First, TVH_Last, TVH_Change,
         SHR_First, SHR_Last, SHR_Change) %>%
  arrange(Field == "Non-sciences", desc(TVH_Last))

build_citizenship_table(df_010, "tab_010", meta,
                        first_year = first_year, last_year = last_year,
                        value_is_share = FALSE,
                        share_group = TRUE,
                        footnote = paste(
                          "Research doctorate recipients by field and citizenship.",
                          "Change is the percent change between", first_year, "and", last_year, ".",
                          "International share is temporary visa holders as a percentage of",
                          "all recipients in the field; its change is relative.",
                          "Fields ordered by 2024 international count; non-sciences shown for comparison."))
```

# Table 11 - Temporary visa holder share of employment by occupation, 2017 / 2021 / 2023 
```{r}
meta <- get_meta("tab_011")

short_names <- c(
  "Biological, agricultural, and other life scientists" = "Biological scientists",
  "Computer and mathematical scientists"                = "Computer/math scientists",
  "Physical and related scientists"                     = "Physical scientists",
  "Social and related scientists"                        = "Social scientists",
  "Engineers"                                            = "Engineers",
  "S&E-related occupations"                               = "S&E-related occupations",
  "Non-S&E occupations"                                   = "Non-S&E occupations"
)

row_order <- c("Computer/math scientists", "Engineers", "Biological scientists",
               "Physical scientists", "Social scientists",
               "S&E-related occupations", "Non-S&E occupations")

df_011 <- read_fig("tab_011") %>%
  mutate(across(-Year, as.numeric)) %>%
  pivot_longer(-Year, names_to = "Occupation", values_to = "Rate") %>%
  filter(!is.na(Rate), Year %in% c(2017, 2019, 2021, 2023)) %>%
  mutate(Rate = Rate * 100,
         Occupation = recode(Occupation, !!!short_names)) %>%
  pivot_wider(names_from = Year, values_from = Rate, names_prefix = "Y") %>%
  mutate(
    Chg2019 = (Y2019 - Y2017) / Y2017 * 100,
    Chg2021 = (Y2021 - Y2019) / Y2019 * 100,
    Chg2023 = (Y2023 - Y2021) / Y2021 * 100,
    Change  = (Y2023 - Y2017) / Y2017 * 100,
    Occupation = factor(Occupation, levels = row_order)
  ) %>%
  arrange(Occupation) %>%
  select(Occupation, Y2017, Chg2019, Chg2021, Chg2023, Y2023, Change)

tab_011 <- build_occupation_share_table(
  df_011, "tab_011", meta,
  level_cols = c("Y2017", "Y2023"),
  chg_cols   = c("Chg2019", "Chg2021", "Chg2023")
)

tab_011
```


# Table 12 - Top H1B Visa Employers in 2017 and 2025
```{r tab_012}
meta <- get_meta("tab_012")

shares <- fig030_shares()

# union of firms that were top-10 in EITHER year
union_firms <- shares %>%
  filter(Year %in% c(2017, 2025)) %>%
  group_by(Year) %>%
  slice_max(Count, n = 10) %>%
  ungroup() %>%
  distinct(Company) %>%
  pull(Company)

wide <- shares %>%
  filter(Year %in% c(2017, 2025), Company %in% union_firms) %>%
  select(Company, Year, Share) %>%
  pivot_wider(names_from = Year, values_from = Share, names_prefix = "Y")

df_012 <- wide %>%
  mutate(
    Company = recode(Company, !!!short_names),
    Y1 = Y2017, Y2 = Y2025,
    Change = if_else(Y2017 > 0, (Y2025 - Y2017) / Y2017 * 100, NA_real_)
  ) %>%
  arrange(desc(Change)) %>%          # order by 2025 share (today's leaders first)
  select(Company, Y1, Y2, Change)

tab_012 <- build_h1b_top10_table(df_012, "tab_012", meta,
                                 first_year = 2017, last_year = 2025)
tab_012
```

# Table 13 
```{r tab_013}
meta <- get_meta("tab_013")

# short row labels -- the raw CSV categories are very long
short_cats <- c(
  "Employed in the U.S. Labor Force in a STEM Occupation Directed Related to Science and Engineering"   = "STEM, directly S&E-related",
  "Employed in the U.S. Labor Force in a STEM Occupation Indirectly Related to Science and Engineering" = "STEM, indirectly S&E-related",
  "Employed in the U.S. Labor Force in a STEM Occupation with a STEM middle skill"                      = "STEM, middle-skill",
  "Employed in the U.S. Labor Force in a non-STEM Occupation"                                            = "Non-STEM occupation",
  "Unemployed in the U.S. Labor Force"                                                                   = "Unemployed",
  "Not in the U.S. labor force"                                                                          = "Not in labor force",
  "Total"                                                                                                = "Total"
)

row_order <- c("STEM, directly S&E-related", "STEM, indirectly S&E-related",
               "STEM, middle-skill", "Non-STEM occupation",
               "Unemployed", "Not in labor force", "Total")

df_013 <- read_fig("fig_025") %>%
  mutate(
    total_n = US_citizen + TPV,
    Citizen = US_citizen / total_n * 100,
    TVH     = TPV / total_n * 100,
    Category = recode(Category, !!!short_cats),
    Category = factor(Category, levels = row_order)
  ) %>%
  arrange(Category) %>%
  select(Category, Citizen, TVH)

tab_013 <- build_labor_citizenship_table(df_013, "tab_013", meta)
tab_013
```

# Export to PDF 
```{r export_pdf, include=FALSE}
library(magick)
library(pdftools)

# ---- Page dimensions ----------------------------------------
page_w_px  <- round(8.5  * 300)
page_h_px  <- round(11.0 * 300)
margin_px  <- round(0.20 * 300)
content_h  <- page_h_px - (margin_px * 2)

# ---- Chart and table manifests ------------------------------
chart_files <- c(
  "fig_001", "fig_002", "fig_003", "fig_004", "fig_005",
  "fig_006", "fig_007", "fig_008", "fig_009", "fig_010",
  "fig_011", "fig_012", "fig_013", "fig_014", "fig_015",
  "fig_016", "fig_017", "fig_018", "fig_019", "fig_020",
  "fig_021", "fig_022", "fig_023", "fig_024", "fig_025",
  "fig_026", "fig_027", "fig_028", "fig_029", "fig_030",
  "fig_031", "fig_032", "fig_033", "fig_034", "fig_035",
  "fig_036", "fig_037",
  "fig_038a", "fig_038b", "fig_038c", "fig_038d",
  "fig_039", "fig_040", "fig_041", "fig_042", "fig_043",
  "fig_044", "fig_045", "fig_046", "fig_047",
  "fig_048",
  "fig_048_acl", "fig_048_acml", "fig_048_aistats", "fig_048_coling",
  "fig_048_colt", "fig_048_corl", "fig_048_cvpr", "fig_048_emnlp",
  "fig_048_iccv", "fig_048_iclr", "fig_048_icml", "fig_048_icra",
  "fig_048_ijcai", "fig_048_iros", "fig_048_naacl", "fig_048_nips",
  "fig_048_rss", "fig_048_siggraphasia", "fig_048_uai", "fig_048_wacv",
  "fig_049", "fig_050", "fig_051", "fig_052", "fig_053",
  "fig_054", "fig_055", "fig_056", "fig_057", "fig_058",
  "fig_059", "fig_060", "fig_061", "fig_062", "fig_063",
  "fig_064", "fig_065", "fig_066", "fig_067", "fig_068",
  "fig_069", "fig_070", "fig_071", "fig_072", "fig_073",
  "fig_074", "fig_075", "fig_076", "fig_077", "fig_078",
  "fig_079", "fig_080", "fig_081", "fig_082", "fig_083",
  "fig_084", "fig_085", "fig_086", "fig_087", "fig_088",
  "fig_089", "fig_090", "fig_091", "fig_092", "fig_093",
  "fig_094", "fig_095", "fig_096", "fig_097", "fig_098",
  "fig_099", "fig_100", "fig_101", "fig_102", "fig_103"
)

table_files <- c(
  "tab_001", "tab_002", "tab_003", "tab_004", "tab_005", "tab_006a", "tab_006b", "tab_006c", "tab_006d"
)

# ---- TOC page count -----------------------------------------
# Calculate upfront so content page numbers are correct from the start
toc_per_page <- 30
n_toc_pages  <- ceiling((length(chart_files) + length(table_files)) / toc_per_page)

# ---- Helper: stamp page number on an image ------------------
stamp_page_number <- function(img, page_num) {
  image_annotate(
    img,
    text     = as.character(page_num),
    gravity  = "South",
    location = "+0+40",
    size     = 36,
    font     = "Source Sans 3",
    color    = "grey50"
  )
}

# ---- Helper: png → list of magick images (one per page) -----
png_to_pages <- function(name, folder) {
  path <- file.path(folder, paste0(name, ".png"))
  if (!file.exists(path)) {
    message("Skipping missing file: ", path)
    return(NULL)
  }

  img  <- image_read(path)
  info <- image_info(img)

  if (info$height > content_h) {
    n_pages <- ceiling(info$height / content_h)
    lapply(seq_len(n_pages), function(i) {
      y_start <- (i - 1) * content_h
      h       <- min(content_h, info$height - y_start)
      slice   <- image_crop(img, paste0(info$width, "x", h, "+0+", y_start))
      page    <- image_blank(page_w_px, page_h_px, color = "white")
      image_composite(page, slice, offset = paste0("+", margin_px, "+", margin_px))
    })
  } else {
    page <- image_blank(page_w_px, page_h_px, color = "white")
    page <- image_composite(page, img, offset = paste0("+", margin_px, "+", margin_px))
    list(page)
  }
}

# ---- Build content pages and collect TOC entries ------------
all_items <- list(
  list(files = chart_files, folder = "final_charts"),
  list(files = table_files, folder = "final_tables")
)

content_pages <- list()
toc_entries   <- list()
page_counter  <- n_toc_pages + 1L

for (group in all_items) {
  for (name in group$files) {
    pages <- png_to_pages(name, group$folder)
    if (is.null(pages)) next

    toc_entries[[length(toc_entries) + 1]] <- list(
      name  = name,
      page  = page_counter,
      title = tryCatch(get_meta(name)$title, error = function(e) name)
    )

    content_pages <- c(content_pages, pages)
    page_counter  <- page_counter + length(pages)
  }
}

# ---- Build TOC as ggplot ------------------------------------
toc_df <- data.frame(
  id    = sapply(toc_entries, `[[`, "name"),
  page  = sapply(toc_entries, `[[`, "page"),
  title = sapply(toc_entries, `[[`, "title"),
  stringsAsFactors = FALSE
)

toc_chunks <- split(toc_df, ceiling(seq_len(nrow(toc_df)) / toc_per_page))

toc_pages <- lapply(seq_along(toc_chunks), function(i) {
  chunk      <- toc_chunks[[i]]
  max_id_len <- max(nchar(chunk$id))

  rows <- mapply(function(id, pg, title) {
    id_pad <- formatC(id,            width = max_id_len, flag = "-")
    pg_str <- formatC(paste0("p.", pg), width = 6,      flag = "-")
    title  <- if (nchar(title) > 60) paste0(substr(title, 1, 57), "...") else title
    paste0(id_pad, "   ", pg_str, "   ", title)
  }, chunk$id, chunk$page, chunk$title)

  heading <- if (i == 1) "Table of Contents" else "Table of Contents (continued)"

  p <- ggplot() +
    annotate("text",
             x = 0.05, y = 0.97,
             label    = heading,
             hjust    = 0, vjust = 1,
             family   = FONT_FAMILY,
             fontface = "bold",
             size     = 7,
             color    = tpa_colors[1]) +
    annotate("segment",
             x = 0.05, xend = 0.95,
             y = 0.955, yend = 0.955,
             color = tpa_colors[1], linewidth = 0.5) +
    annotate("text",
             x = 0.05, y = 0.93,
             label      = paste(rows, collapse = "\n"),
             hjust      = 0, vjust = 1,
             family     = "mono",
             size       = 3.2,
             color      = "grey20",
             lineheight = 1.4) +
    scale_x_continuous(limits = c(0, 1), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
    theme_void() +
    theme(plot.background = element_rect(fill = "white", color = NA))

  tmp <- tempfile(fileext = ".png")
  ggsave(tmp, p, width = 8.5, height = 11, dpi = 300, bg = "white")
  image_read(tmp)
})

# ---- Stamp page numbers -------------------------------------
toc_pages_numbered <- lapply(seq_along(toc_pages), function(i) {
  stamp_page_number(toc_pages[[i]], i)
})

content_pages_numbered <- lapply(seq_along(content_pages), function(i) {
  stamp_page_number(content_pages[[i]], i + n_toc_pages)
})

# ---- Write single-page PDFs then combine --------------------
dir.create("final_charts/tmp_pages", showWarnings = FALSE)

all_pages <- c(toc_pages_numbered, content_pages_numbered)

pdf_paths <- mapply(function(img, i) {
  path <- file.path("final_charts/tmp_pages", sprintf("page_%04d.pdf", i))
  image_write(img, path = path, format = "pdf", density = 300)
  path
}, all_pages, seq_along(all_pages))

pdftools::pdf_combine(unlist(pdf_paths), output = "report.pdf")

# ---- Clean up -----------------------------------------------
file.remove(unlist(pdf_paths))
unlink("final_charts/tmp_pages", recursive = TRUE)

message("Done — ", length(all_pages), " pages written as report.pdf to the project directory")
```
